% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONCLUDE

conclude
}
\vspace*{\stretch{1}}
\begin{center}
CONCLUDE vt. vi. \textipa{[k\textschwa n\textprimstress klu\textlengthmark d]}
\end{center}
vt. 1. 推断出，推论出

After waiting an hour they \textit{concluded} that she wasn't coming.

vt. 2. 结束

He \textit{concluded} his speech by saying that...

vt. 3. 最后，决定

We \textit{concluded} not to go.

vi. 1. 结束，终了

He \textit{concluded} by thanking everyone.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ULTIMATE

ultimate
}
\vspace*{\stretch{1}}
\begin{center}
ULTIMATE a. n. \textipa{[\textprimstress \textturnv ltim\textschwa t]}
\end{center}
a. 1. 最后的，最终的

Their \textit{ultimate} destination was Paris.

n. 1. 最终事物

the \textit{ultimate} of one's desires

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
JUNCTION

junction
}
\vspace*{\stretch{1}}
\begin{center}
JUNCTION n. \textipa{[\textprimstress d\textyogh \textturnv \ng k\textesh \textschwa n]}
\end{center}
1. 联结点，（道路等的）汇合点，枢纽

There's a bridge at the \textit{junction} of the two rivers.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PERSUASION

persuasion
}
\vspace*{\stretch{1}}
\begin{center}
PERSUASION n. \textipa{[p\textschwa \textprimstress swei\textyogh \textschwa n]}
\end{center}
n. 1. 说服（力），劝说

No amount of \textit{persuasion} could move him.

n. 2. 信念，信仰

Many people may be of this \textit{persuasion}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STEREO

stereo
}
\vspace*{\stretch{1}}
\begin{center}
STEREO a. n. \textipa{[\textprimstress steri\textschwa u]}
\end{center}
a. 1. 立体声的

This radio with \textit{stereo} sounds very good.

n. 1. 立体声（装置）

The cinema is equipped with \textit{stereos}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CHIP

chip
}
\vspace*{\stretch{1}}
\begin{center}
CHIP n. vt. \textipa{[t\textesh ip]}
\end{center}
n. 1. 缺口，瑕疵

This glass has a \textit{chip}.

n. 2. 屑片，碎片

The glass broke into \textit{chips}.

vt. 1. 削（或凿）下（屑片或碎片）

\textit{chip} several pieces of stone from the wall

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACID

acid
}
\vspace*{\stretch{1}}
\begin{center}
ACID a. \textipa{[\textprimstress \ae sid]}
\end{center}
1. 酸的，酸味的

That food has an \textit{acid} taste.

2. 尖刻的，刻薄的

His \textit{acid} remarks hurt her feelings.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PROFOUND

profound
}
\vspace*{\stretch{1}}
\begin{center}
PROFOUND a. \textipa{[pr\textschwa \textprimstress faund]}
\end{center}
1. 很深的

She gave a \textit{profound} sigh.

2. 深奥的，渊博的

a \textit{profound} theory

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INDIGNANT

indignant
}
\vspace*{\stretch{1}}
\begin{center}
INDIGNANT a. \textipa{[in\textprimstress dign\textschwa nt]}
\end{center}
1. 愤怒的，愤慨的，义愤的

The actress was \textit{indignant} at the columnist's personal questions.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DOCTRINE

doctrine
}
\vspace*{\stretch{1}}
\begin{center}
DOCTRINE n. \textipa{[\textprimstress d\textopeno ktrin]}
\end{center}
1. 教义，教条，主义

It was one of my father's \textit{doctrines} that pain was good for you.

\vspace*{\stretch{1}}
\end{flashcard}
