% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STRESS

stress
}
\vspace*{\stretch{1}}
\begin{center}
STRESS n. vt. \textipa{[stres]}
\end{center}
n. 1. 压力，紧张

Beethoven produced his most ravishing music at times of personal \textit{stress}.

n. 2. 强调，重要性

The government lays \textit{stress} on welfare work.

vt. 1. 强调，着重

I ought to \textit{stress} the point that this was not a trial but an enquiry.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMPRESSION

impression
}
\vspace*{\stretch{1}}
\begin{center}
IMPRESSION n. \textipa{[im\textprimstress pre\textesh \textschwa n]}
\end{center}
1. 印象，感觉

What are your \textit{impressions} of Shanghai?

2. 印记，压痕

Hard cleaning made no \textit{impression} on the stain.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STRUCTURE

structure
}
\vspace*{\stretch{1}}
\begin{center}
STRUCTURE n. \textipa{[\textprimstress str\textturnv kt\textesh \textschwa]}
\end{center}
1. 结构，构造

The \textit{structure} of the new school is excellent.

2. 建筑物

The laboratory was housed in a temporary wood \textit{structure}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REVOLUTIONARY

revolutionary
}
\vspace*{\stretch{1}}
\begin{center}
REVOLUTIONARY a. \textipa{[\textsecstress rev\textschwa \textprimstress lu\textlengthmark \textesh \textschwa n\textschwa ri]}
\end{center}
1. 革命的，革新的

He was sentenced to 20 year's imprisonment for \textit{revolutionary} activities.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REFRAIN

refrain
}
\vspace*{\stretch{1}}
\begin{center}
REFRAIN v. n. \textipa{[ri\textprimstress frein]}
\end{center}
v. 1. 抑制

She tried to \textit{refrain} from laughing.

n. 1. 叠歌，副歌

They all sang the \textit{refrain}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EMPIRICAL

empirical
}
\vspace*{\stretch{1}}
\begin{center}
EMPIRICAL a. \textipa{[em\textprimstress pirik\textschwa l]}
\end{center}
1. 以经验（或观察）为依据的，经验主义的

That war brings destruction is an \textit{empirical} fact.

2. 经验（上）的，来自经验（或观察）的

The old sailor had never studied navigation, but he had a good \textit{empirical} knowledge of it.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INDICATIVE

indicative
}
\vspace*{\stretch{1}}
\begin{center}
INDICATIVE a. \textipa{[in\textprimstress dik\textschwa tiv]}
\end{center}
1. (of)标示的，指示的，象征的

A headache is sometimes \textit{indicative} of eyestrain.

2. 陈述的，直陈的

There are three moods, \textit{indicative}, imperative and subjunctive in English.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RAW

raw
}
\vspace*{\stretch{1}}
\begin{center}
RAW a. \textipa{[r\textopeno \textlengthmark]}
\end{center}
1. 未煮过的，生的

We can eat carrots cooked or \textit{raw}.

2. 未加工过的

discharge \textit{raw} sewage

3. 生疏无知的，未经训练的

She cursed herself for being so \textit{raw} to believe anything.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EXPANSION

expansion
}
\vspace*{\stretch{1}}
\begin{center}
EXPANSION n. \textipa{[iks\textprimstress p\ae n\textesh \textschwa n]}
\end{center}
1. 扩大，扩张，扩展

The rulers used to have the desire for \textit{expansion}.

2. 膨胀

Heat causes the \textit{expansion} of gas.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DISPLAY

display
}
\vspace*{\stretch{1}}
\begin{center}
DISPLAY vt. n. \textipa{[dis\textprimstress plei]}
\end{center}
vt. 1. 陈列，展览

Shops are \textit{displaying} summer clothes in their windows.

vt. 2. 显示

Nobody \textit{displayed} any interest.

n. 1. 陈列，展览

The goods were on \textit{display} in the store window.

n. 2. 显示

The program became a \textit{display} of personality.

\vspace*{\stretch{1}}
\end{flashcard}
