% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTELLIGENT

intelligent
}
\vspace*{\stretch{1}}
\begin{center}
INTELLIGENT a. \textipa{[in\textprimstress telid\textyogh \textschwa nt]}
\end{center}
1. 聪明的，有才智的

He is a very \textit{intelligent} boy.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CRISIS

crisis
}
\vspace*{\stretch{1}}
\begin{center}
CRISIS n. \textipa{[\textprimstress kraisis]}
\end{center}
1. 危机，危急关头

Because of the drought there is a food \textit{crisis} in many African countries.

2. 决定性时刻，关键阶段

It has been brought to a \textit{crisis}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SOPHISTICATED

sophisticated
}
\vspace*{\stretch{1}}
\begin{center}
SOPHISTICATED a. \textipa{[s\textschwa \textprimstress fistikeitid]}
\end{center}
1. 富有经验的

He is fairly \textit{sophisticated} about biology.

2. 精密的，尖端的

In some ways Canada is more \textit{sophisticated} than its giant southern neighbour.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REWARD

reward
}
\vspace*{\stretch{1}}
\begin{center}
REWARD n. vt. \textipa{[ri\textprimstress w\textopeno \textlengthmark d]}
\end{center}
n. 1. 报答，奖赏

The \textit{rewards} of art are not to be measured in money.

n. 2. 报酬，酬金

The fireman received a \textit{reward} for saving the child's life.

vt. 1. 报答，酬谢，奖励

How can I \textit{reward} your help?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RARELY

rarely
}
\vspace*{\stretch{1}}
\begin{center}
RARELY ad. \textipa{[\textprimstress r\textepsilon \textschwa li]}
\end{center}
1. 不常，难得

They see each other but \textit{rarely}./Only \textit{rarely} do they see each other.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GENERALIZE/-ISE

generalize/-ise
}
\vspace*{\stretch{1}}
\begin{center}
GENERALIZE/-ISE v. \textipa{[\textprimstress d\textyogh en\textschwa r\textschwa laiz]}
\end{center}
1. 概括，归纳

Knowledge is experience \textit{generalized}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FEEBLE

feeble
}
\vspace*{\stretch{1}}
\begin{center}
FEEBLE a. \textipa{[\textprimstress fi\textlengthmark bl]}
\end{center}
1. 虚弱的，无力的

His pulse was very \textit{feeble}.

2. 无效的，无益的

They made a \textit{feeble} resistance to the enemy's attack.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ODOR

odor
}
\vspace*{\stretch{1}}
\begin{center}
ODOR n. \textipa{[\textprimstress \textschwa ud\textschwa]}
\end{center}
1. 气味

A rose has a pleasant \textit{odor}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OPTIMISM

optimism
}
\vspace*{\stretch{1}}
\begin{center}
OPTIMISM n. \textipa{[\textprimstress \textopeno ptimiz\textschwa m]}
\end{center}
1. 乐观，乐观主义

\textit{Optimism} is sometimes dangerous.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BELIEF

belief
}
\vspace*{\stretch{1}}
\begin{center}
BELIEF n. \textipa{[bi\textprimstress li\textlengthmark f]}
\end{center}
1. 相信，信任

I haven't much \textit{belief} in his ability.

2. 信念，信仰

religious or political \textit{beliefs}

\vspace*{\stretch{1}}
\end{flashcard}
