% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CLIMATE

climate
}
\vspace*{\stretch{1}}
\begin{center}
CLIMATE n. \textipa{[\textprimstress klaimit]}
\end{center}
1. 气候，气候区

Retirees often move to a warm \textit{climate}.

2. 风气，气氛

the political \textit{climate}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SIGNIFICANT

significant
}
\vspace*{\stretch{1}}
\begin{center}
SIGNIFICANT a. \textipa{[sig\textprimstress nifik\textschwa nt]}
\end{center}
1. 重要的，意义重大的

A little man may be a very \textit{significant} man.

2. 表示...的(of)

Smiles are \textit{significant} of pleasure.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SURVIVAL

survival
}
\vspace*{\stretch{1}}
\begin{center}
SURVIVAL n. \textipa{[s\textschwa \textprimstress vaiv\textschwa l]}
\end{center}
1. 幸存者；残存物

The old man is a \textit{survival} of a past age.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACTIVITY

activity
}
\vspace*{\stretch{1}}
\begin{center}
ACTIVITY n. \textipa{[\ae k\textprimstress tiv\textschwa ti]}
\end{center}
1. 活动，行动

\textit{Activity} is the test of one's faith.

2. 活跃，活力

There is not quite so much \textit{activity} in the gold market.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TRANSITION

transition
}
\vspace*{\stretch{1}}
\begin{center}
TRANSITION n. \textipa{[tr\ae n\textprimstress si\textyogh \textschwa n]}
\end{center}
1. 过渡，转变

He was still a young intellectual in \textit{transition}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RESPONSIBLE

responsible
}
\vspace*{\stretch{1}}
\begin{center}
RESPONSIBLE a. \textipa{[ri\textprimstress sp\textopeno ns\textschwa bl]}
\end{center}
1. 须负责的，承担责任的

A people's government is \textit{responsible} to the people.

2. 有责任感的，负责可靠的

We must make multinational companies more socially \textit{responsible}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEFICIT

deficit
}
\vspace*{\stretch{1}}
\begin{center}
DEFICIT n. \textipa{[\textprimstress defisit]}
\end{center}
1. 落后，失利

The baseball team erased a 6-0 \textit{deficit}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
UNEMPLOYMENT

unemployment
}
\vspace*{\stretch{1}}
\begin{center}
UNEMPLOYMENT n. \textipa{[\textsecstress \textturnv nim\textprimstress pl\textopeno im\textschwa nt]}
\end{center}
1. 失业（人数）

\textit{Unemployment} will not fall before 1992.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUMMON

summon
}
\vspace*{\stretch{1}}
\begin{center}
SUMMON vt. \textipa{[\textprimstress s\textturnv m\textschwa n]}
\end{center}
1. 召唤

He \textit{summoned} his secretary.

2. 传讯，传唤

I heard myself \textit{summoned} over the loudspeaker to the stationmaster's office.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
NOTORIOUS

notorious
}
\vspace*{\stretch{1}}
\begin{center}
NOTORIOUS a. \textipa{[n\textschwa u\textprimstress t\textopeno \textlengthmark ri\textschwa s]}
\end{center}
1. 臭名昭著的，声名狼藉的

The \textit{notorious} gangster was arrested yesterday.

\vspace*{\stretch{1}}
\end{flashcard}
