% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CYCLE

cycle
}
\vspace*{\stretch{1}}
\begin{center}
CYCLE n. vi. \textipa{[\textprimstress saikl]}
\end{center}
n. 1. 自行车，摩托车

The \textit{cycle} was a gift when he was 16 years old.

n. 2. 循环，周期

The four seasons of the year make a \textit{cycle}.

vi. 1. 骑自行车，骑摩托车

She \textit{cycled} to market.

vi. 2. 循环

Good and bad times \textit{cycle}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SAMPLE

sample
}
\vspace*{\stretch{1}}
\begin{center}
SAMPLE n. vt. \textipa{[\textprimstress s\textscripta \textlengthmark mp\textschwa l]}
\end{center}
n. 1. 样品，标本

Show me \textit{samples} of cloth.

vt. 1. 取样，抽取...的样品

The gourmet is \textit{sampling} the wine.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SPOT

spot
}
\vspace*{\stretch{1}}
\begin{center}
SPOT n. vt. \textipa{[sp\textopeno t]}
\end{center}
n. 1. 斑点，污渍

a \textit{spot} of ink on the paper

n. 2. 地点，处所

He built his house in a beautiful \textit{spot}.

vt. 1. 认出，发现

He was the first to \textit{spot} the danger.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MAINTAIN

maintain
}
\vspace*{\stretch{1}}
\begin{center}
MAINTAIN vt. \textipa{[mein\textprimstress tein]}
\end{center}
1. 维持，保持

The Philippines \textit{maintains} good relations with the United States.

2. 维修，保养

The railway is \textit{maintained} with public funds.

3. 坚持，主张

He \textit{maintains} that he is innocent.

4. 赡养；负担

He \textit{maintains} a large family.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DISASTROUS

disastrous
}
\vspace*{\stretch{1}}
\begin{center}
DISASTROUS a. \textipa{[di\textprimstress z\textscripta \textlengthmark str\textschwa s]}
\end{center}
1. 灾难性的，造成灾害的

Investing his savings in that dubious stock was \textit{disastrous}.

2. 极坏的，很糟的

The aggressors have suffered \textit{disastrous} defeat.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DIFFUSE

diffuse
}
\vspace*{\stretch{1}}
\begin{center}
DIFFUSE v. a. \textipa{[di\textprimstress fju\textlengthmark z]}
\end{center}
v. 1. 扩散，（使）弥漫

The colours of the sunset were \textit{diffused} across the sky.

v. 2. 传播，散布

He so \textit{diffused} his talents that he never became a real success in anything.

a. 1. （文章等）冗长的，漫无边际的

His talk was so \textit{diffuse} that I missed his point.

a. 2. 四散的，弥漫的

an organization which has become \textit{diffuse}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPUTE

compute
}
\vspace*{\stretch{1}}
\begin{center}
COMPUTE v. \textipa{[k\textschwa m\textprimstress pju\textlengthmark t]}
\end{center}
1. 计算，估算

I didn't wish to \textit{compute} that thought further.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONFRONT

confront
}
\vspace*{\stretch{1}}
\begin{center}
CONFRONT vt. \textipa{[k\textschwa n\textprimstress fr\textturnv nt]}
\end{center}
1. (with)使面临，使遇到

The war \textit{confronted} him with hardships.

2. 迎面遇到，面对

When I left the restaurant, I was \textit{confronted} by two men who asked me for money.

3. 使对质，使当面对证

He \textit{confronted} his accuser in court.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CANCER

cancer
}
\vspace*{\stretch{1}}
\begin{center}
CANCER n. \textipa{[\textprimstress k\ae ns\textschwa]}
\end{center}
1. 癌；肿瘤

X-rays are passed through in order to detect a \textit{cancer}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GRANT

grant
}
\vspace*{\stretch{1}}
\begin{center}
GRANT vt. \textipa{[gr\textscripta \textlengthmark nt]}
\end{center}
1. 授予，同意，准予

Mother \textit{granted} me permission to stay overnight.

\vspace*{\stretch{1}}
\end{flashcard}
