% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEPRESS

depress
}
\vspace*{\stretch{1}}
\begin{center}
DEPRESS vt. \textipa{[di\textprimstress pres]}
\end{center}
1. 使沮丧，使消沉

He was \textit{depressed} by the bad news.

2. 按下

She \textit{depressed} the keys of the piano.

3. 减少，降低

The thermometer was \textit{depressed} to fifteen below.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
WEAKEN

weaken
}
\vspace*{\stretch{1}}
\begin{center}
WEAKEN v. \textipa{[\textprimstress wi\textlengthmark k\textschwa n]}
\end{center}
1. （使）变弱，（使）减弱

They have never \textit{weakened} their stand for human rights.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FEMININE

feminine
}
\vspace*{\stretch{1}}
\begin{center}
FEMININE a. \textipa{[\textprimstress feminin]}
\end{center}
1. 女性的，妇女的

the \textit{feminine} members of society

2. 娇柔的，女子气的

He is a bit \textit{feminine}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BREAKTHROUGH

breakthrough
}
\vspace*{\stretch{1}}
\begin{center}
BREAKTHROUGH n. \textipa{[\textprimstress breik\texttheta ru\textlengthmark]}
\end{center}
1. 突破，突破性进展，重要的新发现

The armoured forces will be exploiting a \textit{breakthrough} and rapidly overrunning the enemy seaboard.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TERRIFY

terrify
}
\vspace*{\stretch{1}}
\begin{center}
TERRIFY vt. \textipa{[\textprimstress terifai]}
\end{center}
1. 使害怕，使惊吓

She was \textit{terrified} out of her wits.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONSERVATION

conservation
}
\vspace*{\stretch{1}}
\begin{center}
CONSERVATION n. \textipa{[\textsecstress k\textopeno ns\textschwa \textprimstress vei\textesh \textschwa n]}
\end{center}
1. 保存，保护

\textit{Conservation} of water is of great importance in desert areas.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FEMALE

female
}
\vspace*{\stretch{1}}
\begin{center}
FEMALE n. a. \textipa{[\textprimstress fi\textlengthmark meil]}
\end{center}
n. 1. 雌性的动物

Is it a male or \textit{female}?

a. 1. 雌的，女（性）的

They had their first \textit{female} child.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FAKE

fake
}
\vspace*{\stretch{1}}
\begin{center}
FAKE n. vt. a \textipa{[feik]}
\end{center}
n. 1. 假货，赝品

The antique is a \textit{fake}.

n. 2. 骗子，冒充者

a medical \textit{fake}

vt. 1. 伪造；伪装，假装

The whole story was \textit{faked}.

\textit{fake} a yawn to dissemble embarrassment

a. 1. 假的，伪造的

These diamonds are \textit{fake}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTRIGUE

intrigue
}
\vspace*{\stretch{1}}
\begin{center}
INTRIGUE n. vi. vt. \textipa{[in\textprimstress tri\textlengthmark g]}
\end{center}
n. 1. 阴谋，诡计，密谋

be accustomed to \textit{intrigue} and deception

vi. 1. 耍阴谋，施诡计

They are \textit{intriguing} against the government.

vt. 1. 激起...的好奇心（或兴趣），迷住

The book's unusual title \textit{intrigued} me into reading it.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
WEB

web
}
\vspace*{\stretch{1}}
\begin{center}
WEB n. \textipa{[web]}
\end{center}
1. （蜘蛛等的）网

the \textit{webs} of the silkworm

2. 网络，错综复杂的事务

Who can understand the \textit{web} of life?

\vspace*{\stretch{1}}
\end{flashcard}
