% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BENEFIT

benefit
}
\vspace*{\stretch{1}}
\begin{center}
BENEFIT n. vt. vi. \textipa{[\textprimstress benifit]}
\end{center}
n. 1. 益处，好处

I say this with the \textit{benefit} of hindsight.

n. 2. 救济金，保险金

These people draw unemployment \textit{benefits}.

vt. 1. 有益于

Moderate exercise will \textit{benefit} you.

vi. 1. 得益

I \textit{benefited} from his advice.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GENERALLY

generally
}
\vspace*{\stretch{1}}
\begin{center}
GENERALLY ad. \textipa{[\textprimstress d\textyogh en\textschwa r\textschwa li]}
\end{center}
1. 一般，通常

Elections are held \textit{generally} every other year.

2. 普遍地，广泛地

It was once \textit{generally} believed that...

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ARGUMENT

argument
}
\vspace*{\stretch{1}}
\begin{center}
ARGUMENT n. \textipa{[\textprimstress \textscripta \textlengthmark gjum\textschwa nt]}
\end{center}
1. 争论，争吵，辩论

We got into an \textit{argument} about whether to go by sea or by air.

2. 理由，论据，论点

His \textit{argument} in favor of the plan was persuasive.

3. 说理，论证

I did not follow his \textit{argument}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INDEPENDENT

independent
}
\vspace*{\stretch{1}}
\begin{center}
INDEPENDENT a. \textipa{[\textsecstress indi\textprimstress pend\textschwa nt]}
\end{center}
1. 独立的，自主的，自立的

His elder daughter is completely \textit{independent}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTUITION

intuition
}
\vspace*{\stretch{1}}
\begin{center}
INTUITION n. \textipa{[\textsecstress intju(\textlengthmark)\textprimstress i\textesh \textschwa n]}
\end{center}
1. 直觉知识，直觉真理

Those \textit{intuitions} are quite correct.

2. 直觉

powers of \textit{intuition}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SCRUTINY

scrutiny
}
\vspace*{\stretch{1}}
\begin{center}
SCRUTINY n. \textipa{[\textprimstress skru\textlengthmark tini]}
\end{center}
1. 详细检查，仔细观察

The \textit{scrutiny} of his papers revealed a lot of cheating.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STYLISH

stylish
}
\vspace*{\stretch{1}}
\begin{center}
STYLISH a. \textipa{[\textprimstress staili\textesh]}
\end{center}
1. 时髦的，入时的，漂亮的

The girls wore \textit{stylish} clothes.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ALTERNATIVE

alternative
}
\vspace*{\stretch{1}}
\begin{center}
ALTERNATIVE n. a. \textipa{[\textopeno \textlengthmark l\textprimstress t\textschwa \textlengthmark n\textschwa tiv]}
\end{center}
n. 1. 取舍，供选择的东西

That's the only \textit{alternative}.

n. 2. 选择的自由，选择的余地

I have no \textit{alternative} but to go.

a. 1. 两者择一的，供选择的

the \textit{alternative} plans of having a picnic or taking a boat trip

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BUDGET

budget
}
\vspace*{\stretch{1}}
\begin{center}
BUDGET n. vi. a. \textipa{[\textprimstress b\textturnv d\textyogh it]}
\end{center}
n. 1. 预算，预算拨款

The Finance Minister will introduce/open a new \textit{budget} in April.

vi. 1. (for)编预算，做安排

\textit{budget} for the coming year

a. 1. 低廉的，收费公道的

a \textit{budget} price

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STREAM

stream
}
\vspace*{\stretch{1}}
\begin{center}
STREAM n. v. \textipa{[stri\textlengthmark m]}
\end{center}
n. 1. 小河，溪流

He jumped across the \textit{stream}.

n. 2. 流，一股，一串

A \textit{stream} of people issued from the theatre.

v. 1. 流（出），涌（出）

The pipe broke and water \textit{streamed} onto the floor.

\vspace*{\stretch{1}}
\end{flashcard}
