% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RELIGIOUS

religious
}
\vspace*{\stretch{1}}
\begin{center}
RELIGIOUS a. \textipa{[ri\textprimstress lid\textyogh \textschwa s]}
\end{center}
1. 宗教的

Mozart's profoundly \textit{religious} music

2. 笃信宗教的，虔诚的

He is a truly \textit{religious} man who goes to church every day.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EMOTION

emotion
}
\vspace*{\stretch{1}}
\begin{center}
EMOTION n. \textipa{[i\textprimstress m\textschwa u\textesh \textschwa n]}
\end{center}
1. 情感，激情

Love, hate, fear and anger are \textit{emotions}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MALE

male
}
\vspace*{\stretch{1}}
\begin{center}
MALE a. n. \textipa{[meil]}
\end{center}
a. 1. 男（性）的，雄的

He is a member of the \textit{male} chorus.

n. 1. 男子，雄性动物，雄性植物

Is the horse a \textit{male} or a female?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
POLLUTION

pollution
}
\vspace*{\stretch{1}}
\begin{center}
POLLUTION n. \textipa{[p\textschwa \textprimstress lu\textlengthmark \textesh \textschwa n]}
\end{center}
1. 污染，污染物

\textit{Pollution} in the air reduced the visibility near the airport.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LITERACY

literacy
}
\vspace*{\stretch{1}}
\begin{center}
LITERACY n. \textipa{[\textprimstress lit\textschwa r\textschwa si]}
\end{center}
1. 识字，有文化，读写能力

He has a little \textit{literacy}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VERSATILE

versatile
}
\vspace*{\stretch{1}}
\begin{center}
VERSATILE a. \textipa{[\textprimstress v\textschwa \textlengthmark s\textschwa tail]}
\end{center}
1. 多才多艺的，有多种技能的

He was a \textit{versatile} writer.

2. 有多种用途的，多功能的，万用的

a \textit{versatile} new kitchen machine

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUCCESSOR

successor
}
\vspace*{\stretch{1}}
\begin{center}
SUCCESSOR n. \textipa{[s\textschwa k\textprimstress ses\textschwa]}
\end{center}
1. 接替的人或事物，继任者

Mr. Jones is the headmaster's \textit{successor}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GREEDY

greedy
}
\vspace*{\stretch{1}}
\begin{center}
GREEDY a. \textipa{[\textprimstress gri\textlengthmark di]}
\end{center}
1. 贪吃的，嘴馋的

She is not hungry but \textit{greedy}.

2. 贪婪的，贪心的

He is \textit{greedy} of/for money.

3. 渴望的

She was always \textit{greedy} for knowledge, and at last became an expert in the field of languages.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONTACT

contact
}
\vspace*{\stretch{1}}
\begin{center}
CONTACT vt. \textipa{[k\textschwa n\textprimstress t\ae kt]} n. \textipa{[\textprimstress k\textopeno nt\ae kt]}
\end{center}
vt. 1. 接触，联系

Our patrols on all our fronts \textit{contacted} no enemy today.

n. 1. 接触，联络，联系

The pilot lost \textit{contact} with his base.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONSUME

consume
}
\vspace*{\stretch{1}}
\begin{center}
CONSUME vt. \textipa{[k\textschwa n\textprimstress sju\textlengthmark m]}
\end{center}
1. 消耗，花费

In the mid-seventies Americans \textit{consumed} about seventeen million barrels of oil daily.

2. 耗资

His purchase of books \textit{consumed} all of the scholar's income.

\vspace*{\stretch{1}}
\end{flashcard}
