% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SPECIES

species
}
\vspace*{\stretch{1}}
\begin{center}
SPECIES n. \textipa{[\textprimstress spi\textlengthmark \textesh i\textlengthmark z]}
\end{center}
1. 种，类

He has a \textit{species} of cunning.

2. 『生』(物)种

There are more than two hundred and fifty \textit{species} of shark.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ORGANIZATION

organization
}
\vspace*{\stretch{1}}
\begin{center}
ORGANIZATION n. \textipa{[\textsecstress \textopeno \textlengthmark g\textschwa nai\textprimstress zei\textesh \textschwa n]}
\end{center}
1. 条理，系统

The \textit{organization} of the painting is quite remarkable.

2. 组织

The \textit{organization} of a large-scale garden party takes time and thought.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VIOLENCE

violence
}
\vspace*{\stretch{1}}
\begin{center}
VIOLENCE n. \textipa{[\textprimstress vai\textschwa l\textschwa ns]}
\end{center}
1. 暴力

rule with \textit{violence}

2. 猛烈，剧烈，强烈

He flung open the door with unnecessary \textit{violence}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BEHAVIOR

behavior
}
\vspace*{\stretch{1}}
\begin{center}
BEHAVIOR n. \textipa{[bi\textprimstress heivj\textschwa]}
\end{center}
1. 行为，举止，表现

His \textit{behavior} at the party was good.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ECONOMIC

economic
}
\vspace*{\stretch{1}}
\begin{center}
ECONOMIC a. \textipa{[\textsecstress i\textlengthmark k\textschwa \textprimstress n\textopeno mik]}
\end{center}
1. 合算的，有利可图的

There was uranium in sufficient quantity to make mining \textit{economic}.

2. 经济上的

\textit{economic} decline

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ENVIRONMENT

environment
}
\vspace*{\stretch{1}}
\begin{center}
ENVIRONMENT n. \textipa{[in\textprimstress vai\textschwa r\textschwa nm\textschwa nt]}
\end{center}
1. 环境，周围状况；自然环境

He grew up in an \textit{environment} of poverty.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTERVIEW

interview
}
\vspace*{\stretch{1}}
\begin{center}
INTERVIEW n. \textipa{[\textprimstress int\textschwa vju\textlengthmark]}
\end{center}
1. 接见，会见

He granted an \textit{interview} to her.

2. 面谈，面试

He had a job \textit{interview} that morning.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EVIDENCE

evidence
}
\vspace*{\stretch{1}}
\begin{center}
EVIDENCE n. \textipa{[\textprimstress evid\textschwa ns]}
\end{center}
1. 根据，证据

Have you any \textit{evidence} for this statement?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FASHION

fashion
}
\vspace*{\stretch{1}}
\begin{center}
FASHION n. \textipa{[\textprimstress f\ae \textesh \textschwa n]}
\end{center}
1. 方式，样子

He joined his hands together in Indian \textit{fashion} and gave a little bow.

2. 流行款式，时新式样，时装

It is no longer the \textit{fashion} to curtsey in greeting people.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CURRENT

current
}
\vspace*{\stretch{1}}
\begin{center}
CURRENT n. a. \textipa{[\textprimstress k\textturnv r\textschwa nt]}
\end{center}
n. 1. （空气、水等的）流，潮流

Television influences the \textit{current} of thought.

n. 2. 趋势，倾向

Newspapers influence the \textit{current} of public opinion.

a. 1. 现时的，当前的

\textit{current} events

a. 2. 通行的，流行的

A rumour is \textit{current} that school will close tommorrow.

\vspace*{\stretch{1}}
\end{flashcard}
