% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PROFIT

profit
}
\vspace*{\stretch{1}}
\begin{center}
PROFIT n. vt. vi. \textipa{[\textprimstress pr\textopeno fit]}
\end{center}
n. 1. 利润，收益，益处

Their investment plan will give an estimated \textit{profit} of \textsterling 1 millions.

vt. 1. 有益于，有利于

It will \textit{profit} you nothing to do that.

vi. 1. 得益

Speculators \textit{profit} from changes in prices.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ISSUE

issue
}
\vspace*{\stretch{1}}
\begin{center}
ISSUE n. v. \textipa{[\textprimstress isju\textlengthmark]}
\end{center}
n. 1. 问题，争论点

There was no \textit{issue} at all between us.

n. 2. 发行，（书刊的）期号

the March \textit{issue} of the magazine.

v. 1. 发行，颁布，出版

A flood of currency \textit{issued} each year.

v. 2. （使）流出，发出

A blue flicker \textit{issued} from the gas cooker.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMPACT

impact
}
\vspace*{\stretch{1}}
\begin{center}
IMPACT n. \textipa{[\textprimstress imp\ae kt]}
\end{center}
1. 影响，作用

the \textit{impact} of new ideas of the race

2. 冲击，碰撞

The car hit the stone wall with great \textit{impact}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RECOGNIZE

recognize
}
\vspace*{\stretch{1}}
\begin{center}
RECOGNIZE vt. \textipa{[\textprimstress rek\textschwa gnaiz]}
\end{center}
1. 认出，识别

The child \textit{recognized} the word.

2. 承认，认可

I \textit{recognize} that he is cleverer than I am.

3. 赏识，表彰；报偿

The manager \textit{recognized} the employees' worth by giving them a bonus.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FUNCTION

function
}
\vspace*{\stretch{1}}
\begin{center}
FUNCTION n. vi. \textipa{[\textprimstress f\textturnv \ng k\textesh \textschwa n]}
\end{center}
n. 1. 功能，机能，作用

Each object has a single \textit{function}.

n. 2. 职务，职责

the \textit{functions} of a policeman

n. 3. 函数

In y=5x, y is a \textit{function} of x.

vi. 1. 运行，起作用

An attributive noun \textit{functions} as an adjective.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONFIRM

confirm
}
\vspace*{\stretch{1}}
\begin{center}
CONFIRM vt. \textipa{[k\textschwa n\textprimstress f\textschwa \textlengthmark m]}
\end{center}
1. 证实，肯定

Please \textit{confirm} your reservations 48 hours in advance.

2. 进一步确定

This letter is to \textit{confirm} your appointment.

3. 批准，确认

We have \textit{confirmed} the treaty.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONSPICUOUS

conspicuous
}
\vspace*{\stretch{1}}
\begin{center}
CONSPICUOUS a. \textipa{[k\textschwa n\textprimstress spikju\textschwa s]}
\end{center}
1. 显眼的，明显的

He took a \textit{conspicuous} seat near the entrance.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EXTINCT

extinct
}
\vspace*{\stretch{1}}
\begin{center}
EXTINCT a. \textipa{[ik\textprimstress sti\ng kt]}
\end{center}
1. 灭绝的，绝种的

This kind of mammal is becoming \textit{extinct}.

2. （火山等）熄灭了的

There is an \textit{extinct} volcano over there.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONSERVE

conserve
}
\vspace*{\stretch{1}}
\begin{center}
CONSERVE vt. \textipa{[k\textschwa n\textprimstress s\textschwa \textlengthmark v]}
\end{center}
1. 保藏，保存

He \textit{conserved} his energy for the game.

2. 保护

It is everybody's duty to \textit{conserve} natural resources.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HOIST

hoist
}
\vspace*{\stretch{1}}
\begin{center}
HOIST vt. \textipa{[h\textopeno ist]}
\end{center}
1. 举起，升起，吊起

They \textit{hoisted} Henry to their shoulders in shouting triumph.

\vspace*{\stretch{1}}
\end{flashcard}
