% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TYPICAL

typical
}
\vspace*{\stretch{1}}
\begin{center}
TYPICAL a. \textipa{[\textprimstress tipik\textschwa l]}
\end{center}
1. 典型的，有代表性的

The painting is a \textit{typical} Rembrandt.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ENSURE

ensure
}
\vspace*{\stretch{1}}
\begin{center}
ENSURE vt. \textipa{[in\textprimstress \textesh u\textschwa]}
\end{center}
1. 保证，担保，确保

His industry and ability will \textit{ensure} his success.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONTEND

contend
}
\vspace*{\stretch{1}}
\begin{center}
CONTEND vi. vt. \textipa{[k\textschwa n\textprimstress tend]}
\end{center}
vi. 1. 搏斗，争斗

His wife's ill health is something he has to \textit{contend} with.

vi. 2. 争夺，竞争

I \textit{contended} with him for the prize.

vt. 1. 声称，主张

He \textit{contends} that it is not true.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REAP

reap
}
\vspace*{\stretch{1}}
\begin{center}
REAP vi. \textipa{[ri\textlengthmark p]}
\end{center}
1. 收割，收获

The men were all out \textit{reaping}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BADGE

badge
}
\vspace*{\stretch{1}}
\begin{center}
BADGE n. \textipa{[b\ae d\textyogh]}
\end{center}
1. 徽章，证章

Policemen and firemen wear \textit{badges}.

2. 标记，标识

The war veteran considers his scar a \textit{badge} of honor.

3. 象征

Chains are a \textit{badge} of slavery.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONTEXT

context
}
\vspace*{\stretch{1}}
\begin{center}
CONTEXT n. \textipa{[\textprimstress k\textopeno ntekst]}
\end{center}
1. 背景，环境

It is in such a \textit{context} that the military took over.

2. 上下文，语境

Taken in \textit{context}, his remarks make some sense.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ELSEWHERE

elsewhere
}
\vspace*{\stretch{1}}
\begin{center}
ELSEWHERE ad. \textipa{[\textsecstress els\textprimstress w\textepsilon \textschwa]}
\end{center}
1. 在别处，到别处

The species is found \textit{elsewhere}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INDUCE

induce
}
\vspace*{\stretch{1}}
\begin{center}
INDUCE vt. \textipa{[in\textprimstress dju\textlengthmark s]}
\end{center}
1. 引起，导致

The author by his choice of words has \textit{induced} a particular frame of mind in the reader.

2. 引诱，劝

Advertisements \textit{induce} people to buy.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AGGRAVATE

aggravate
}
\vspace*{\stretch{1}}
\begin{center}
AGGRAVATE vt. \textipa{[\textprimstress \ae gr\textschwa veit]}
\end{center}
1. 加重，加剧，使恶化

Smoking \textit{aggravates} a cold.

2. 激怒，使恼火

Don't \textit{aggravate} your father by persistent goading.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPACT

compact
}
\vspace*{\stretch{1}}
\begin{center}
COMPACT a. \textipa{[\textprimstress k\textopeno mp\ae kt]} vt. \textipa{[k\textschwa m\textprimstress p\ae kt]}
\end{center}
a. 1. 紧凑的，小巧的，袖珍的

a \textit{compact} shopping centre

vt. 1. 把...压实（或塞实），使坚实

Racial and religious similarities \textit{compacted} the tribes into a nation.

\vspace*{\stretch{1}}
\end{flashcard}
