% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ENHANCE

enhance
}
\vspace*{\stretch{1}}
\begin{center}
ENHANCE vt. \textipa{[in\textprimstress h\textscripta \textlengthmark ns]}
\end{center}
1. 提高（质量、价值、吸引力等），增加，增强，增进

The book is \textit{enhanced} with illustrative photographs.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CHINA

china
}
\vspace*{\stretch{1}}
\begin{center}
CHINA n. \textipa{[\textprimstress t\textesh ain\textschwa]}
\end{center}
1. 瓷器，陶瓷

He has a collection of \textit{china}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AUTHORIZE/ISE

authorize/ise
}
\vspace*{\stretch{1}}
\begin{center}
AUTHORIZE/ISE vt. \textipa{[\textprimstress \textopeno \textlengthmark \texttheta \textschwa raiz]}
\end{center}
1. 批准，认可，准许

The dictionary \textit{authorizes} two spellings for this word.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONTRADICT

contradict
}
\vspace*{\stretch{1}}
\begin{center}
CONTRADICT vt. \textipa{[\textsecstress k\textopeno ntr\textschwa \textprimstress dikt]}
\end{center}
1. 反驳，否认...的真实性

He \textit{contradicted} his own statement.

2. 与...发生矛盾，与...抵触

The facts \textit{contradict} his theory.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ABNORMAL

abnormal
}
\vspace*{\stretch{1}}
\begin{center}
ABNORMAL a. \textipa{[\ae b\textprimstress n\textopeno \textlengthmark m\textschwa l]}
\end{center}
1. 反常的，异常的

It is \textit{abnormal} to eat so much.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EFFICIENT

efficient
}
\vspace*{\stretch{1}}
\begin{center}
EFFICIENT a. \textipa{[i\textprimstress fi\textesh \textschwa nt]}
\end{center}
1. 效率高的，有能力的

Sailors are amazingly \textit{efficient} souvenir hunters.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMPLICATION

implication
}
\vspace*{\stretch{1}}
\begin{center}
IMPLICATION n. \textipa{[\textsecstress impli\textprimstress kei\textesh \textschwa n]}
\end{center}
1. 含义，暗示，暗指

What are the \textit{implications} of this statement?

2. 卷入，牵连

We heard of his \textit{implication} in a conspiracy.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PONDER

ponder
}
\vspace*{\stretch{1}}
\begin{center}
PONDER v. \textipa{[\textprimstress p\textopeno nd\textschwa]}
\end{center}
1. 思考，考虑，沉思

She \textit{pondered} her next words.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AXIS

axis
}
\vspace*{\stretch{1}}
\begin{center}
AXIS n. \textipa{[\textprimstress \ae ksis]}
\end{center}
1. 轴，轴线

The Earth turns around its own \textit{axis} once in twenty-four hours.

2. 构图中心线

The diameter of a circle is an \textit{axis}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CATASTROPHE

catastrophe
}
\vspace*{\stretch{1}}
\begin{center}
CATASTROPHE n. \textipa{[k\textschwa \textprimstress t\ae str\textschwa fi]}
\end{center}
1. 大灾难，灾祸

The earthquake was a terrible \textit{catastrophe}.

\vspace*{\stretch{1}}
\end{flashcard}
