% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INCREASINGLY

increasingly
}
\vspace*{\stretch{1}}
\begin{center}
INCREASINGLY ad. \textipa{[in\textprimstress kri\textlengthmark si\ng li]}
\end{center}
1. 日益，越来越多地

\textit{Increasingly}, people are realizing that our basic problems are educational ones.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AUTHORITY

authority
}
\vspace*{\stretch{1}}
\begin{center}
AUTHORITY n. \textipa{[\textopeno \textlengthmark \textprimstress \texttheta \textopeno r\textschwa ti]}
\end{center}
1. 权威

A good dictionary is an \textit{authority} on the meanings of words.

2. 当权者

The \textit{authority} asked me why Tom wasn't in school.

3. 权利，管辖权

Who is in \textit{authority} here?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HAMPER

hamper
}
\vspace*{\stretch{1}}
\begin{center}
HAMPER vt. \textipa{[\textprimstress h\ae mp\textschwa]}
\end{center}
1. 妨碍，阻碍

Ice floes \textit{hamper} barge traffic on the Elbe River.

2. 束缚，限制

Why do you want to go and \textit{hamper} yourself with such a man?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMMENCE

commence
}
\vspace*{\stretch{1}}
\begin{center}
COMMENCE vi. vt. \textipa{[k\textschwa \textprimstress mens]}
\end{center}
vi. 1. 开始

The play will \textit{commence} at eight o'clock.

vt. 1. 使开始，着手

He has \textit{commenced} studying law.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CLOSET

closet
}
\vspace*{\stretch{1}}
\begin{center}
CLOSET n. vt. a. \textipa{[\textprimstress kl\textopeno zit]}
\end{center}
n. 1. 橱，壁橱

He hung his raincoat in the hall \textit{closet}.

vt. 1. 把...引进密室会谈

He was \textit{closeted} with the manager for three hours.

a. 1. 私下的，秘密的

They had a \textit{closet} consultation before they reached an agreement.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
THREAT

threat
}
\vspace*{\stretch{1}}
\begin{center}
THREAT n. \textipa{[\texttheta ret]}
\end{center}
1. 威胁，恐吓

Because of death \textit{threats} he moved to a secluded spot.

2. 凶兆，征兆

There was a \textit{threat} of winter in the air.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MOTIVATE

motivate
}
\vspace*{\stretch{1}}
\begin{center}
MOTIVATE vt. \textipa{[\textprimstress m\textschwa utiveit]}
\end{center}
1. 激励

One of the most important things that teachers have to do in their teaching is to \textit{motivate} students, not force them to learn.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTRINSIC

intrinsic
}
\vspace*{\stretch{1}}
\begin{center}
INTRINSIC a. \textipa{[in\textprimstress trinsik]}
\end{center}
1. 固有的，本质的，内在的

There is no \textit{intrinsic} shortage of water in England.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MARGINAL

marginal
}
\vspace*{\stretch{1}}
\begin{center}
MARGINAL a. \textipa{[\textprimstress m\textscripta \textlengthmark d\textyogh in\textschwa l]}
\end{center}
1. 微小的，少量的，不重要的

There's only a \textit{marginal} difference between the two estimates.

2. 最低限度的

\textit{marginal} income

3. 记在页边的

While reading, she often makes \textit{marginal} notes.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CORRUPT

corrupt
}
\vspace*{\stretch{1}}
\begin{center}
CORRUPT a. v. \textipa{[k\textschwa \textprimstress t\textturnv pt]}
\end{center}
a. 1. 堕落的，腐败的，贪赃舞弊的

\textit{Corrupt} friends led him astray.

v. 1. 腐蚀，堕落

The new rulers soon became \textit{corrupt}.

\vspace*{\stretch{1}}
\end{flashcard}
