% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PERCEPTION

perception
}
\vspace*{\stretch{1}}
\begin{center}
PERCEPTION n. \textipa{[p\textschwa \textprimstress sep\textesh \textschwa n]}
\end{center}
1. 感知，觉察（力）

He was scared by the completeness of her \textit{perception}.

2. 认识，观念，看法

What is your \textit{perception} of his campaign policy?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REGION

region
}
\vspace*{\stretch{1}}
\begin{center}
REGION n. \textipa{[\textprimstress ri\textlengthmark d\textyogh \textschwa n]}
\end{center}
1. 地区，地带，区域

This sort of flower blooms only in the tropical \textit{regions}.

2. 范围，幅度

In what \textit{region} is the price likely to be?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUBSIDIARY

subsidiary
}
\vspace*{\stretch{1}}
\begin{center}
SUBSIDIARY a. n. \textipa{[s\textschwa b\textprimstress sidi\textschwa ri]}
\end{center}
a. 1. 辅助的，次要的

The work that women are allocated is frequently of a type perceived as \textit{subsidiary} to that of men.

n. 1. 子公司，附属机构

Our company has a \textit{subsidiary} in Austria.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TURBULENT

turbulent
}
\vspace*{\stretch{1}}
\begin{center}
TURBULENT a. \textipa{[\textprimstress t\textschwa \textlengthmark bjul\textschwa nt]}
\end{center}
1. 动荡的，混乱的

a \textit{turbulent} childhood

2. 汹涌的

We were frightened by the \textit{turbulent} ocean during the storm.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HURRICANE

hurricane
}
\vspace*{\stretch{1}}
\begin{center}
HURRICANE n. \textipa{[\textprimstress h\textturnv rik\textschwa n]}
\end{center}
1. 飓风

The \textit{hurricane} blew with such force that trees were uprooted.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMPLY

imply
}
\vspace*{\stretch{1}}
\begin{center}
IMPLY vt. \textipa{[im\textprimstress plai]}
\end{center}
1. 暗示，含有...的意思

His silence \textit{implied} consent.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MINIMUM

minimum
}
\vspace*{\stretch{1}}
\begin{center}
MINIMUM n. a. \textipa{[\textprimstress minim\textschwa m]}
\end{center}
n. 1. 最低限度，最少量

We want to spend a \textit{minimum} of both time and money in building the bridge.

a. 1. 最低的，最小的

Before going abroad, you need a \textit{minimum} deposit of \$20,000.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONCEIVE

conceive
}
\vspace*{\stretch{1}}
\begin{center}
CONCEIVE vi. vt. \textipa{[k\textschwa n\textprimstress si\textlengthmark v]}
\end{center}
\normalsize vi. 1. (of)构想出，设想

\footnotesize When did scientists first \textit{conceive} of space travel?

\normalsize vi. 2. 怀孕

\footnotesize She was told she couldn't \textit{conceive}.

\normalsize vt. 1. 认为

\footnotesize He \textit{conceived} it his duty to do so.

\normalsize vt. 2. 构想出，设想

\footnotesize I can't \textit{conceive} why you did that.

\normalsize vt. 3. 怀（胎）

\footnotesize The child was \textit{conceived} on the night of their wedding.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TRANSISTOR

transistor
}
\vspace*{\stretch{1}}
\begin{center}
TRANSISTOR n. \textipa{[tr\ae n\textprimstress sist\textschwa]}
\end{center}
1. 晶体管，晶体管收音机

a highly sophisticated \textit{transistor}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CLUSTER

cluster
}
\vspace*{\stretch{1}}
\begin{center}
CLUSTER n. vi. \textipa{[\textprimstress kl\textturnv st\textschwa]}
\end{center}
1. （果实、花等的）串，簇，（人或物等的）群，组

Here and there in the suburbs are newly built houses in \textit{clusters}.

2. 群集，丛生

The girls \textit{clustered} around their teacher.

\vspace*{\stretch{1}}
\end{flashcard}
