% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACTION

action
}
\vspace*{\stretch{1}}
\begin{center}
ACTION n. \textipa{[\textprimstress \ae k\textesh \textschwa n]}
\end{center}
1. 行动，行动过程

He is all \textit{action} now.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACCOUNT

account
}
\vspace*{\stretch{1}}
\begin{center}
ACCOUNT n. vi. \textipa{[\textschwa \textprimstress kaunt]}
\end{center}
\normalsize n. 1. 叙述，说明；账，账户

\footnotesize The book presents an unbiased \textit{account} of the historical event.

\footnotesize The \textit{accounts} show that they have spent more than they received.

\normalsize vi. 1. 解释，说明；导致，引起；（在数量、比例方面）占

\footnotesize He could not \textit{account} for the time spent away from his post.

\footnotesize Late frosts \textit{accounted} for the poor fruit crop.

\footnotesize The region \textit{accounts} for a large part of usable timber.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRIORITY

priority
}
\vspace*{\stretch{1}}
\begin{center}
PRIORITY n. \textipa{[prai\textprimstress \textopeno r\textschwa ti]}
\end{center}
1. 优先（权），重点

Fire engines and ambulances have \textit{priority} over other traffic.

2. 优先考虑的事

Education is a top \textit{priority} in the nation.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ASSERT

assert
}
\vspace*{\stretch{1}}
\begin{center}
ASSERT vt. \textipa{[\textschwa \textprimstress s\textschwa \textlengthmark t]}
\end{center}
1. 肯定地说，断言

He \textit{asserted} his ideas loudly and clearly.

2. 维护，坚持

He \textit{asserted} his belief that she was not guilty.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FLIP

flip
}
\vspace*{\stretch{1}}
\begin{center}
FLIP vt. n. a. \textipa{[flip]}
\end{center}
\normalsize vt. 1. 快速翻动，转动；快速猛然移动（某物）；捻掷（硬币），轻抛

\footnotesize \textit{flip} pages in a book

\footnotesize She \textit{flipped} the light on.

\footnotesize Let's \textit{flip} a coin to see who goes first.

\normalsize n. 1. 轻弹，轻抛

\footnotesize He removed the crumb with a \textit{flip} of the thumb and forefinger.

\normalsize a. 1. 无礼的，轻率的，轻浮的

\footnotesize He always gave \textit{flip} answers to serious questions.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BANDAGE

bandage
}
\vspace*{\stretch{1}}
\begin{center}
BANDAGE n. vt. \textipa{[\textprimstress b\ae ndid\textyogh]}
\end{center}
n. 1. 绷带

She covered the cut on my finger with a \textit{bandage}.

vt. 1. 用绷带扎缚

You should \textit{bandage} your wounded leg.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SENSITIVE

sensitive
}
\vspace*{\stretch{1}}
\begin{center}
SENSITIVE a. \textipa{[\textprimstress sensitiv]}
\end{center}
1. (to)敏感的

We need to be more \textit{sensitive} to the needs of the young students.

2. 神经过敏的，容易生气的

She is \textit{sensitive} to criticism.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
WRITER

writer
}
\vspace*{\stretch{1}}
\begin{center}
WRITER n. \textipa{[\textprimstress rait\textschwa]}
\end{center}
1. 作者，著者

a film \textit{writer}-director

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SECURE

secure
}
\vspace*{\stretch{1}}
\begin{center}
SECURE a. vt. \textipa{[si\textprimstress kju\textschwa]}
\end{center}
\normalsize a. 1. 有把握的，确定无疑的；牢固的，稳固的；无忧虑的，安心的

\footnotesize His promotion in the army is \textit{secure}.

\footnotesize It is on a \textit{secure} foundation.

\footnotesize She felt \textit{secure} only when both doors were locked.

\normalsize vt. 1. 得到，获得；使安全，保卫；缚牢

\footnotesize He's lucky to have \textit{secured} himself such a good job.

\footnotesize The regiment \textit{secured} its position while awaiting the enemy attack.

\footnotesize They \textit{secured} all the windows as the storm began.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SURPASS

surpass
}
\vspace*{\stretch{1}}
\begin{center}
SURPASS vt. \textipa{[s\textschwa \textprimstress p\textscripta \textlengthmark s]}
\end{center}
1. 超过，优于，多于

His work/performance \textit{surpassed} (all) expectations.

2. 超过...的界限，非...所能办到（或理解）

The task \textit{surpassed} his skill.

\vspace*{\stretch{1}}
\end{flashcard}
