% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BACTERIA

bacteria
}
\vspace*{\stretch{1}}
\begin{center}
BACTERIA n. \textipa{[b\ae k\textprimstress ti\textschwa ri\textschwa]}
\end{center}
1. [bacterium的复数]细菌

A new \textit{bacteria} has appeared.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LANE

lane
}
\vspace*{\stretch{1}}
\begin{center}
LANE n. \textipa{[lein]}
\end{center}
1. （乡间）小路，小巷

Two women were gossiping in the \textit{lane}.

2. 车道，跑到

The road is divided into three \textit{lanes}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SURVIVE

survive
}
\vspace*{\stretch{1}}
\begin{center}
SURVIVE vi. vt. \textipa{[s\textschwa \textprimstress vaiv]}
\end{center}
vi. 1. 活下来，幸存

She is Britain's longest \textit{surviving} transplant patient.

vt. 1. 从...中逃出，从（困境中）挺过来

Only two people \textit{survived} the fire.

vt. 2. 比...活得长

She \textit{survived} her husband by three years.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DECADE

decade
}
\vspace*{\stretch{1}}
\begin{center}
DECADE n. \textipa{[\textprimstress dekeid]}
\end{center}
1. 十年，十年期

The custom has prevailed for \textit{decades}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PERCEIVE

perceive
}
\vspace*{\stretch{1}}
\begin{center}
PERCEIVE v. \textipa{[p\textschwa \textprimstress si\textlengthmark v]}
\end{center}
1. 察觉，感知

He was only able to \textit{perceive} light and colour; he could not see properly.

2. 认识到，意识到，理解

He may \textit{perceive} himself a loser.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VITAMIN

vitamin
}
\vspace*{\stretch{1}}
\begin{center}
VITAMIN n. \textipa{[\textprimstress vit\textschwa min]}
\end{center}
1. 维生素

\textit{Vitamins} are essential to the nourishment of the body.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REVENGE

revenge
}
\vspace*{\stretch{1}}
\begin{center}
REVENGE n. vt. \textipa{[ri\textprimstress vend\textyogh]}
\end{center}
n. 1. 报复，报仇

Man may destroy the balance of nature, but, from time to time, nature takes a terrible \textit{revenge}.

vt. 1. 为...报仇，报...之仇

He \textit{revenged} his brother's murder.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MASCULINE

masculine
}
\vspace*{\stretch{1}}
\begin{center}
MASCULINE a. \textipa{[\textprimstress m\textscripta \textlengthmark skjulin]}
\end{center}
1. 男性的，男子的

Rugby is a purely \textit{masculine} sport; I cannot even imagine a women's rugby team!

2. 男子气概的

She looks rather \textit{masculine} in that suit.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HUMANITY

humanity
}
\vspace*{\stretch{1}}
\begin{center}
HUMANITY n. \textipa{[hju(\textlengthmark)\textprimstress m\ae n\textschwa ti]}
\end{center}
1. 人类，[总称]人

\textit{Humanity} in bathing suits covered the sand.

2. 人性

\textit{Humanity} is a mixture of good and bad qualities.

3. 人道，博爱，仁慈

They treated the prisoners with \textit{humanity}.

4. [pl.]人文学科

The \textit{humanities} have eight departments.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LITERAL

literal
}
\vspace*{\stretch{1}}
\begin{center}
literal a. \textipa{[\textprimstress lit\textschwa r\textschwa l]}
\end{center}
1. 照字面的

The word is to be understood in a poetic, not a \textit{literal} sense.

2. 逐字的

He made a \textit{literal} interpretation.

\vspace*{\stretch{1}}
\end{flashcard}
