% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INSTRUMENT

instrument
}
\vspace*{\stretch{1}}
\begin{center}
INSTRUMENT n. \textipa{[\textprimstress instrum\textschwa nt]}
\end{center}
1. 仪器，器械，工具

The newspaper is an \textit{instrument} of mass communication.

2. 乐器

He accompanied her singing on a lute-like \textit{instrument}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MOLECULE

molecule
}
\vspace*{\stretch{1}}
\begin{center}
MOLECULE n. \textipa{[\textprimstress m\textopeno likju\textlengthmark l]}
\end{center}
1. 分子

A \textit{molecule} of water consists of two atoms of hydrogen and one atom of oxygen.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AMOUNT

amount
}
\vspace*{\stretch{1}}
\begin{center}
AMOUNT n. vi. \textipa{[\textschwa \textprimstress maunt]}
\end{center}
n. 1. 数量，数额，总数

What is the \textit{amount} of my bill?

vi. 1. (to)合计，共计

Building costs \textit{amount} to six million dollars.

vi. 2. 等同，接近

This \textit{amounts} to doing the whole thing over again.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ADDITION

addition
}
\vspace*{\stretch{1}}
\begin{center}
ADDITION n. \textipa{[\textschwa \textprimstress di\textesh \textschwa n]}
\end{center}
1. 加

The \textit{addition} of flour will thicken gravy.

2. 增加的人（或物）

He will be a most valuable \textit{addition} to our board.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ASCRIBE

ascribe
}
\vspace*{\stretch{1}}
\begin{center}
ASCRIBE vt. \textipa{[\textschwa \textprimstress skraib]}
\end{center}
1. 把...归因于

They \textit{ascribed} his success to good luck.

2. 把...归属于

This invention is \textit{ascribed} to Edison.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EXPIRE

expire
}
\vspace*{\stretch{1}}
\begin{center}
EXPIRE vi. \textipa{[ik\textprimstress spai\textschwa]}
\end{center}
1. 期满，（期限）终止

His term of office \textit{expires} this year.

2. 断气，死亡

The old man \textit{expired} at the age of eighty.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REPEL

repel
}
\vspace*{\stretch{1}}
\begin{center}
REPEL vt. \textipa{[ri\textprimstress pel]}
\end{center}
1. 击退，逐回

We \textit{repeled} the enemy.

2. 排斥

The positive poles of two magnets \textit{repel} each other.

3. 使厌恶

His manner \textit{repels} me.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CORRELATE

correlate
}
\vspace*{\stretch{1}}
\begin{center}
CORRELATE vi. vt. \textipa{[\textprimstress k\textopeno rileit]}
\end{center}
vi. 1. (to, with)相关，关联

A person's happiness sometimes \textit{correlates} closely to the amount of sunshine he receives.

vt. 1. 使互相关联

\textit{correlate} activities in the lab and the field

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SPEAKER

speaker
}
\vspace*{\stretch{1}}
\begin{center}
SPEAKER n. \textipa{[\textprimstress spi\textlengthmark k\textschwa]}
\end{center}
1. 说话者，演讲者

Sometimes the listener takes over the talk and becomes the \textit{speaker}.

2. 将某种语言的人

English \textit{speakers} of French.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ELEMENT

element
}
\vspace*{\stretch{1}}
\begin{center}
ELEMENT n. \textipa{[\textprimstress elim\textschwa nt]}
\end{center}
1. 元素

Both bydrogen and oxygen are \textit{elements}, but water is not.

2. 成分，要素，元件

A good story has an \textit{element} of suspense.

\vspace*{\stretch{1}}
\end{flashcard}
