% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RANGE

range
}
\vspace*{\stretch{1}}
\begin{center}
RANGE n. vi. \textipa{[reind\textyogh]}
\end{center}
n. 1. 幅度，范围

There are three basic salary \textit{ranges}.

n. 2. 走向

The \textit{range} of the strata is east and west.

vi. 1. （在某范围内）变动，变化

Prices \textit{range} from \$25 to \$75.

vi. 2. (over)论及，涉及

His talk \textit{ranged} over a variety of matters.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BACKGROUND

background
}
\vspace*{\stretch{1}}
\begin{center}
BACKGROUND n. \textipa{[\textprimstress b\ae kgraund]}
\end{center}
1. 出身背景；经历

I have not the technical \textit{background} to understand the subject.

2. 背景资料

I need more \textit{background} (information) before I can help you.

3. （画等的）背景，底子

The election took place against a \textit{background} of widespread unemployment.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AFFECT

affect
}
\vspace*{\stretch{1}}
\begin{center}
AFFECT vt. \textipa{[\textschwa \textprimstress fekt]}
\end{center}
1. 影响

The change has seriously \textit{affected} his income.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BILLION

billion
}
\vspace*{\stretch{1}}
\begin{center}
BILLION n. \textipa{[\textprimstress bilj\textschwa n]}
\end{center}
1. 十亿

The factory has just made a \$ 1 billion contract with a Japanese car company.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CRITICAL

critical
}
\vspace*{\stretch{1}}
\begin{center}
CRITICAL a. \textipa{[\textprimstress kritik\textschwa l]}
\end{center}
1. 决定性的，关键性的，危急的

The girl is now in a \textit{critical} condition.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CATER

cater
}
\vspace*{\stretch{1}}
\begin{center}
CATER v. \textipa{[\textprimstress keit\textschwa]}
\end{center}
1. (for, to)满足需要（或欲望），迎合

We're going to \textit{cater} to your every desire.

2. 提供饮食及服务

We don't need your kitchen. We'll have everything \textit{catered}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HATCH

hatch
}
\vspace*{\stretch{1}}
\begin{center}
HATCH vt. vi. \textipa{[h\ae t\textesh]}
\end{center}
vt. 1. 孵出，孵

Who knows how to \textit{hatch} chickens?

vt. 2. 酝酿；图谋

\textit{hatch} (out) a plot

vi. 1. （小鸡等）出壳，孵出

When will these eggs \textit{hatch} (out)?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TEMPERAMENT

temperament
}
\vspace*{\stretch{1}}
\begin{center}
TEMPERAMENT n. \textipa{[\textprimstress temp\textschwa r\textschwa m\textschwa nt]}
\end{center}
1. 气质，性格

He is highly nervous and volatile in \textit{temperament}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONTAMINATE

contaminate
}
\vspace*{\stretch{1}}
\begin{center}
CONTAMINATE vt. \textipa{[k\textschwa n\textprimstress t\ae mineit]}
\end{center}
1. 弄脏，污染

Fumes \textit{contaminate} the air.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DIPLOMA

diploma
}
\vspace*{\stretch{1}}
\begin{center}
DIPLOMA n. \textipa{[di\textprimstress pl\textschwa um\textschwa]}
\end{center}
1. 毕业文凭，学位证书

He is studying at an evening school for a \textit{diploma}.

\vspace*{\stretch{1}}
\end{flashcard}
