% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ECONOMY

economy
}
\vspace*{\stretch{1}}
\begin{center}
ECONOMY n. \textipa{[i\textprimstress k\textopeno n\textschwa mi]}
\end{center}
1. 经济

It was a blow to the \textit{economies} of both towns.

2. 节约，节省

By various little \textit{economies}, she managed to save some money.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EXECUTIVE

executive
}
\vspace*{\stretch{1}}
\begin{center}
EXECUTIVE a. n. \textipa{[ig\textprimstress zekjutiv]}
\end{center}
a. 1. 善于经营管理的

His wife has grown \textit{executive} and used to command.

n. 1. 总经理；常务董事

He is an \textit{executive} in this bank.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PROCESS

process
}
\vspace*{\stretch{1}}
\begin{center}
PROCESS n. \textipa{[\textprimstress pr\textschwa uses]}
\end{center}
1. 过程，进程

He is quick in his thought \textit{processes}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONCERN

concern
}
\vspace*{\stretch{1}}
\begin{center}
CONCERN n. vt. \textipa{[k\textschwa n\textprimstress s\textschwa \textlengthmark n]}
\end{center}
n. 1. 关切的事，有关的事

The energy problem is an important \textit{concern} for all of us.

n. 2. 关心，担心

The parents showed great \textit{concern} for the boy.

vt. 1. 涉及，有关

He is said to have been \textit{concerned} in the crime.

vt. 2. 使关心，使担心

Don't \textit{concern} yourself about his future.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ABILITY

ability
}
\vspace*{\stretch{1}}
\begin{center}
ABILITY n. \textipa{[\textschwa \textprimstress bil\textschwa ti]}
\end{center}
1. 能力

The \textit{ability} to be clearly heard is extremely important for newsreaders.

2. 能耐

Man has the \textit{ability} to speak.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMMUNITY

community
}
\vspace*{\stretch{1}}
\begin{center}
COMMUNITY n. \textipa{[k\textschwa \textprimstress mju\textlengthmark n\textschwa ti]}
\end{center}
1. 社会，公众

He did it for the good of the \textit{community}.

2. 团体，界

a \textit{community} of retired people

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPETITION

competition
}
\vspace*{\stretch{1}}
\begin{center}
COMPETITION n. \textipa{[\textsecstress k\textopeno mpi\textprimstress ti\textesh \textschwa n]}
\end{center}
1. 竞争，比赛

There's a lot of \textit{competition} for this job.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CRIME

crime
}
\vspace*{\stretch{1}}
\begin{center}
CRIME n. \textipa{[kraim]}
\end{center}
1. 罪，罪行，犯罪

He was convicted of the \textit{crime} of embezzling.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CREATE

create
}
\vspace*{\stretch{1}}
\begin{center}
CREATE vt. \textipa{[kri(\textlengthmark)\textprimstress eit]}
\end{center}
1. 创造，创作

God \textit{created} Eve from one of Adam's ribs.

2. 引起，产生

Her arrival \textit{created} a terrible confusion.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMMERCIAL

commercial
}
\vspace*{\stretch{1}}
\begin{center}
COMMERCIAL a. n. \textipa{[k\textschwa \textprimstress m\textschwa \textlengthmark \textesh \textschwa l]}
\end{center}
a. 1. 商业的，商务的

He does not want to make a living in the \textit{commercial} world.

a. 2. 商品化的，商业性的

They found oil in \textit{commercial} quantities.

n. 1. 商业广告

There are many \textit{commercials} on TV.

\vspace*{\stretch{1}}
\end{flashcard}
