% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PROMOTE

promote
}
\vspace*{\stretch{1}}
\begin{center}
PROMOTE vt. \textipa{[pr\textschwa \textprimstress m\textschwa ut]}
\end{center}
1. 促进，发扬

Swimming \textit{promotes} health.

2. 提升，提拔

He was \textit{promoted} to the rank of captain.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HIGHLY

highly
}
\vspace*{\stretch{1}}
\begin{center}
HIGHLY ad. \textipa{[\textprimstress haili]}
\end{center}
1. 高度地，极，非常

This is \textit{highly} improbable.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STAFF

staff
}
\vspace*{\stretch{1}}
\begin{center}
STAFF n. vt. \textipa{[st\textscripta \textlengthmark f]}
\end{center}
n. 1. 全体职工，全体人员

The company has got a \textit{staff} of about 40.

vt. 1. 为...配备工作人员

The labs are \textit{staffed} by/with engineers and physicists.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EVOLUTION

evolution
}
\vspace*{\stretch{1}}
\begin{center}
EVOLUTION n. \textipa{[\textsecstress i\textlengthmark v\textschwa \textprimstress lu\textlengthmark \textesh \textschwa n]}
\end{center}
1. 进化，演化

Current life on earth is a consequence of the law on \textit{evolution}.

2. 发展，演变

This is a book about the \textit{evolution} of the steamship.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INSIGHT

insight
}
\vspace*{\stretch{1}}
\begin{center}
INSIGHT n. \textipa{[\textprimstress insait]}
\end{center}
1. 洞悉，深刻见解

He has given me an \textit{insight} into Russian literature.

2. 洞察力

She has a woman's quick \textit{insight} into character.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PREMISE

premise
}
\vspace*{\stretch{1}}
\begin{center}
PREMISE n. \textipa{[\textprimstress premis]}
\end{center}
1. [pl.]（企业、机构等使用的）房屋连地基，经营场址

The firm moved to their new \textit{premises}.

2. 前提，假设

They are the major and minor \textit{premises} on which the conclusion is based.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DISTORT

distort
}
\vspace*{\stretch{1}}
\begin{center}
DISTORT vt. \textipa{[dis\textprimstress t\textopeno \textlengthmark t]}
\end{center}
1. 歪曲，曲解

The reporter \textit{distorted} the facts.

2. 扭曲，使变形

His face was \textit{distorted} with pain.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FACILITATE

facilitate
}
\vspace*{\stretch{1}}
\begin{center}
FACILITATE vt. \textipa{[f\textschwa \textprimstress siliteit]}
\end{center}
1. 使变得（更）容易，使便利

Such a port would \textit{facilitate} the passage of oil from the Middle East to Japan.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VEIL

veil
}
\vspace*{\stretch{1}}
\begin{center}
VEIL n. vt. \textipa{[veil]}
\end{center}
n. 1. 面纱，面罩

a bridal \textit{veil}

n. 2. 遮盖物，掩饰物

A \textit{veil} of mist hid the mountain.

vt. 1. 遮盖，掩饰

She \textit{veiled} her beautiful face.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACCORDING

according
}
\vspace*{\stretch{1}}
\begin{center}
ACCORDING ad. \textipa{[\textschwa \textprimstress k\textopeno \textlengthmark di\ng]}
\end{center}
1. 依照

The players are speaking and moving \textit{according} to the director's instructions.

\vspace*{\stretch{1}}
\end{flashcard}
