% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TECHNOLOGY

technology
}
\vspace*{\stretch{1}}
\begin{center}
TECHNOLOGY n. \textipa{[tek\textprimstress n\textopeno l\textschwa d\textyogh i]}
\end{center}
1. 科技

The development of \textit{technology} has been very fast.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PHYSICAL

physical
}
\vspace*{\stretch{1}}
\begin{center}
PHYSICAL a. \textipa{[\textprimstress fizikl]}
\end{center}
1. 自然的，自然科学的

It's a \textit{physical} impossibility for man to fly like birds.

2. 身体的，肉体的

He is in good \textit{physical} condition.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CLAIM

claim
}
\vspace*{\stretch{1}}
\begin{center}
CLAIM vt. n. \textipa{[kleim]}
\end{center}
vt. 1. 声称，主张

Don't \textit{claim} to know what you don't know.

vt. 2. 需要，值得

The matter \textit{claims} our attention.

vt. 3. 对...提出要求，索取

They \textit{claimed} on the carriers for the loss involved.

n. 1. 要求；主张，断言

The present era makes great \textit{claims} upon us.

He made no \textit{claims} to sound scholarship.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HEEL

heel
}
\vspace*{\stretch{1}}
\begin{center}
HEEL n. \textipa{[hi\textlengthmark l]}
\end{center}
1. （鞋、袜等的）后跟

She was wearing high \textit{heels}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RESPONSIBILITY

responsibility
}
\vspace*{\stretch{1}}
\begin{center}
RESPONSIBILITY n. \textipa{[ri\textsecstress sp\textopeno ns\textschwa \textprimstress bil\textschwa ti]}
\end{center}
1. 责任，责任心

A doctor has a \textit{responsibility} to his patients.

2. 职责，义务

We must take the \textit{responsibility} of defending our country.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HARD

hard
}
\vspace*{\stretch{1}}
\begin{center}
HARD a. \textipa{[h\textscripta \textlengthmark d]}
\end{center}
1. 坚硬的

The ground is too \textit{hard} to dig.

2. 困难的

She is \textit{hard} to please.

3. 艰苦的

The nation had a \textit{hard} time.

4. 冷酷的，严厉的

a \textit{hard} judge

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CRIMINAL

criminal
}
\vspace*{\stretch{1}}
\begin{center}
CRIMINAL n. a. \textipa{[\textprimstress krimin\textschwa l]}
\end{center}
n. 1. 罪犯，犯人

The \textit{criminal} was arrested by the policeman.

a. 1. 犯罪的，刑事的

He has no \textit{criminal} record.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PLANET

planet
}
\vspace*{\stretch{1}}
\begin{center}
PLANET n. \textipa{[\textprimstress pl\ae nit]}
\end{center}
1. 行星

A \textit{planet} is a heavenly body that moves around the Sun.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BIOGRAPHY

biography
}
\vspace*{\stretch{1}}
\begin{center}
BIOGRAPHY n. \textipa{[bai\textprimstress \textopeno gr\textschwa fi]}
\end{center}
1. 传记

He gave me several \textit{biographies} of the Prophet Muhammad.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
APPEARANCE

appearance
}
\vspace*{\stretch{1}}
\begin{center}
APPEARANCE n. \textipa{[\textschwa \textprimstress pi\textschwa r\textschwa ns]}
\end{center}
1. 出现，显露，露面

New banks and post offices all made their \textit{appearance} in the next two decades.

2. 外观，外貌，外表

He was most particular about his \textit{appearance}.

\vspace*{\stretch{1}}
\end{flashcard}
