% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MANUFACTURER

manufacturer
}
\vspace*{\stretch{1}}
\begin{center}
MANUFACTURER n. \textipa{[\textsecstress m\ae nju\textprimstress f\ae kt\textesh \textschwa r\textschwa]}
\end{center}
1. 制造商，制造厂

These faulty goods should be sent back to the \textit{manufacturer}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SOMEWHAT

somewhat
}
\vspace*{\stretch{1}}
\begin{center}
SOMEWHAT ad. \textipa{[\textprimstress s\textturnv mhw\textopeno t]}
\end{center}
1. 稍微，有点儿

It is \textit{somewhat} difficult to answer this question.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ADVOCATE

advocate
}
\vspace*{\stretch{1}}
\begin{center}
ADVOCATE vt. \textipa{[\textprimstress \ae dv\textschwa keit]} n. \textipa{[\textprimstress \ae dv\textschwa kit]}
\end{center}
vt. 1. 拥护，提倡，主张

The professor \textit{advocates} building more schools than roads.

n. 1. 拥护者，提倡者

He is an \textit{advocate} of peace.

n. 2. 辩护人，律师

He hired the best \textit{advocate} he could find to represent him in court.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INEVITABLE

inevitable
}
\vspace*{\stretch{1}}
\begin{center}
INEVITABLE a. \textipa{[in\textprimstress evit\textschwa bl]}
\end{center}
1. 不可避免的，必然（发生）的

Death is \textit{inevitable}; it comes to everyone.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GAZE

gaze
}
\vspace*{\stretch{1}}
\begin{center}
GAZE v. n. \textipa{[geiz]}
\end{center}
v. 1. 凝视，注视

He \textit{gazed} at the ceiling for a long time.

n. 1. 凝视，注视

Her \textit{gaze} was fixed on him.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DISABLE

disable
}
\vspace*{\stretch{1}}
\begin{center}
DISABLE vt. \textipa{[dis\textprimstress eibl]}
\end{center}
1. 使丧失能力，使伤残

John was permanently \textit{disabled}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPENSATE

compensate
}
\vspace*{\stretch{1}}
\begin{center}
COMPENSATE v. \textipa{[\textprimstress k\textopeno mp\textschwa nseit]}
\end{center}
1. 补偿，弥补，抵消

The firm \textit{compensated} the injured worker for the time lost.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRESTIGE

prestige
}
\vspace*{\stretch{1}}
\begin{center}
PRESTIGE n. \textipa{[pres\textprimstress ti\textlengthmark \textyogh]}
\end{center}
1. 威信，威望

He is an author of international \textit{prestige}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMMEMORATE

commemorate
}
\vspace*{\stretch{1}}
\begin{center}
COMMEMORATE vt. \textipa{[k\textschwa \textprimstress mem\textschwa reit]}
\end{center}
1. 纪念，庆祝

They built a tower to \textit{commemorate} their victory.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FINALLY

finally
}
\vspace*{\stretch{1}}
\begin{center}
FINALLY ad. \textipa{[\textprimstress fain\textschwa li]}
\end{center}
1. 最后，终于

The lost pen was \textit{finally} found.

\vspace*{\stretch{1}}
\end{flashcard}
