% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SOURCE

source
}
\vspace*{\stretch{1}}
\begin{center}
SOURCE n. \textipa{[s\textopeno \textlengthmark s]}
\end{center}
1. 原因

These sharks are a \textit{source} of worry on the beach.

2. 来源，出处

Have they found the \textit{source} of the gas leak?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FEATURE

feature
}
\vspace*{\stretch{1}}
\begin{center}
FEATURE n. \textipa{[\textprimstress fi\textlengthmark t\textesh \textschwa]}
\end{center}
1. 特征，特色

The island's chief \textit{feature} was its beauty.

2. [pl.]面貌，相貌

She has charming \textit{features}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RATE

rate
}
\vspace*{\stretch{1}}
\begin{center}
RATE n. \textipa{[reit]}
\end{center}
1. 速度，进度

At your present \textit{rate} of working, you won't finish before midnight.

2. 等级

This is a first-\textit{rate} hotel.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ORIGINAL

original
}
\vspace*{\stretch{1}}
\begin{center}
ORIGINAL a. \textipa{[\textschwa \textprimstress rid\textyogh \textschwa nl]}
\end{center}
1. 起初的，原先的

Philadelphia was the \textit{original} capital of the United States.

2. 独创的，新颖的

The inventor had an \textit{original} mind.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RECENTLY

recently
}
\vspace*{\stretch{1}}
\begin{center}
RECENTLY ad. \textipa{[\textprimstress ri\textlengthmark s\textschwa ntli]}
\end{center}
1. 最近，新近

I haven't heard from her \textit{recently}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REVEAL

reveal
}
\vspace*{\stretch{1}}
\begin{center}
REVEAL vt. \textipa{[ri\textprimstress vi\textlengthmark l]}
\end{center}
1. 揭露，泄露

That question \textit{revealed} the truth.

2. 展现，显示

She drew the curtains aside to \textit{reveal} a beautiful garden.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HEMISPHERE

hemisphere
}
\vspace*{\stretch{1}}
\begin{center}
HEMISPHERE n. \textipa{[\textprimstress hemisfi\textschwa]}
\end{center}
1. （地球的）半球

The northern half of the Earth is the Northern \textit{Hemisphere}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INCENTIVE

incentive
}
\vspace*{\stretch{1}}
\begin{center}
INCENTIVE n. \textipa{[in\textprimstress sentiv]}
\end{center}
1. 刺激，鼓励

He hasn't much \textit{incentive}/many \textit{incentives} to work hard.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUBORDINATE

subordinate
}
\vspace*{\stretch{1}}
\begin{center}
SUBORDINATE n. a. \textipa{[s\textschwa \textprimstress b\textopeno \textlengthmark din\textschwa t]} vt. \textipa{[s\textschwa \textprimstress b\textopeno \textlengthmark dineit]}
\end{center}
n. 1. 部属，下级

He treated his \textit{subordinates} like slaves.

a. 1. (to)次要的

All other questions are \textit{subordinate} to this one.

a. 2. 下级的，隶属的

In the army captains are \textit{subordinates} to majors.

vt. 1. 把...列入下级，使隶属

He \textit{subordinated} his own interests to the objectives of the company.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PREVALENT

prevalent
}
\vspace*{\stretch{1}}
\begin{center}
PREVALENT a. \textipa{[\textprimstress prev\textschwa l\textschwa nt]}
\end{center}
1. 流行的，普遍的

Smog is more \textit{prevalent} in urban centres.

\vspace*{\stretch{1}}
\end{flashcard}
