% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CHEMICAL

chemical
}
\vspace*{\stretch{1}}
\begin{center}
CHEMICAL a. \textipa{[\textprimstress kemik\textschwa l]}
\end{center}
1. 化学的

A \textit{chemical} change takes place in any substance when it burns.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FOCUS

focus
}
\vspace*{\stretch{1}}
\begin{center}
FOCUS v. n. \textipa{[\textprimstress f\textschwa uk\textschwa s]}
\end{center}
v. 1. (on)（使）聚焦，（使）集中

The beams of light \textit{focused} on the aircraft.

n. 1. 焦点，（注意、活动、兴趣等的）中心

China is becoming the \textit{focus} of the world attention.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MORAL

moral
}
\vspace*{\stretch{1}}
\begin{center}
MORAL n. a. \textipa{[\textprimstress m\textopeno r\textschwa l]}
\end{center}
n. 1. [pl.]道德，品行，道德规范

a standard of \textit{morals}

a. 1. 道德（上）的，有道德的

The story of my father is a sad \textit{moral} tale.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
POWERFUL

powerful
}
\vspace*{\stretch{1}}
\begin{center}
POWERFUL a. \textipa{[\textprimstress pau\textschwa ful]}
\end{center}
1. 强大的，有力的，有权的

He is a \textit{powerful} politician in this district.

2. 强壮的，强健的

She is a \textit{powerful} swimmer.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VULNERABLE

vulnerable
}
\vspace*{\stretch{1}}
\begin{center}
VULNERABLE a. \textipa{[\textprimstress v\textturnv ln\textschwa r\textschwa bl]}
\end{center}
1. 易受伤的，脆弱的

That country is economically \textit{vulnerable}, but militarily a colossus.

2. 易受攻击的，难防御的

We were asked to leave that \textit{vulnerable} bridge.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTENSIFY

intensify
}
\vspace*{\stretch{1}}
\begin{center}
INTENSIFY v. \textipa{[in\textprimstress tensifai]}
\end{center}
1. （使）增强，（使）变尖锐

The drought has \textit{intensified}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TEMPT

tempt
}
\vspace*{\stretch{1}}
\begin{center}
TEMPT vt. \textipa{[tempt]}
\end{center}
1. 吸引，引起...的兴趣

Their unfriendliness \textit{tempted} me to leave the party.

2. 引诱，诱惑

Nothing could \textit{tempt} me to take such a step.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INSTALLMENT

installment
}
\vspace*{\stretch{1}}
\begin{center}
INSTALLMENT n. \textipa{[in\textprimstress st\textopeno \textlengthmark lm\textschwa nt]}
\end{center}
1. 分期付款，分期交付

I paid for the car in \textit{installments}.

2. （分期连载的）部分

The novel will appear in fifteen \textit{installments} in \textit{Tianjin Daily}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COSTUME

costume
}
\vspace*{\stretch{1}}
\begin{center}
COSTUME n. \textipa{[\textprimstress k\textopeno stju\textlengthmark m]}
\end{center}
1. 戏装

actors wearing historical \textit{costume}

2. （一个时期或一个国家中流行的）服装，服饰

We're going to the party in eighteenth-century \textit{costume}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ENTRY

entry
}
\vspace*{\stretch{1}}
\begin{center}
ENTRY n. \textipa{[\textprimstress entri]}
\end{center}
1. 入口处，河口，通道

At the \textit{entry} to the bridge stand two imposing pillars.

2. 登记，登录

He made an \textit{entry} in his diary every night.

3. 进入

He managed to gain \textit{entry} to an exclusive club.

4. 参赛的人（或物），参赛者名单

He was their country's official \textit{entry}.

\vspace*{\stretch{1}}
\end{flashcard}
