% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SYSTEM

system
}
\vspace*{\stretch{1}}
\begin{center}
SYSTEM n. \textipa{[\textprimstress sist\textschwa m]}
\end{center}
1. 系统，体系

We have a large \textit{system} of railway.

2. 制度，体制

What \textit{system} of government do you have in your country?

3. 条理，秩序

He works with/by \textit{system}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SOCIAL

social
}
\vspace*{\stretch{1}}
\begin{center}
SOCIAL a. \textipa{[\textprimstress s\textschwa u\textesh \textschwa l]}
\end{center}
1. 社会的

The family is a \textit{social} unit.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INDIVIDUAL

individual
}
\vspace*{\stretch{1}}
\begin{center}
INDIVIDUAL a. n. \textipa{[\textsecstress indi\textprimstress vidju\textschwa l]}
\end{center}
a. 1. 个别的，单独的

Each \textit{individual} leaf on the tree is different.

a. 2. 独特的

There was nothing \textit{individual} about him except a deep scar across his right cheek.

n. 1. 个人

the freedom of the \textit{individual}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CULTURE

culture
}
\vspace*{\stretch{1}}
\begin{center}
CULTURE n. \textipa{[\textprimstress k\textturnv lt\textesh \textschwa]}
\end{center}
1. 文化，文明

A child should be exposed to \textit{culture} at an early age.

2. 教养，修养

a man of great \textit{culture}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
NUCLEAR

nuclear
}
\vspace*{\stretch{1}}
\begin{center}
NUCLEAR a. \textipa{[\textprimstress nju\textlengthmark kli\textschwa]}
\end{center}
1. 核子的，核能的，核武器的

China stands for prohibition and destruction of \textit{nuclear} weapons.

2. 核心的，中心的

A family consisting only of a husband, wife and children, without grandparents, aunts, uncles, etc., is called a \textit{nuclear} family.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONFLICT

conflict
}
\vspace*{\stretch{1}}
\begin{center}
CONFLICT n. \textipa{[\textprimstress k\textopeno nflikt]} vi. \textipa{[k\textschwa n\textprimstress flikt]}
\end{center}
n. 1. 争论；抵触；冲突

They came into sharp \textit{conflict} over the wording of the message.

vi. 1. 冲突；抵触

The two accounts of what had happened \textit{conflict} (with each other).

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRODUCT

product
}
\vspace*{\stretch{1}}
\begin{center}
PRODUCT n. \textipa{[\textprimstress pr\textopeno d\textturnv kt]}
\end{center}
1. 产品，产物；乘积

The market sells food \textit{products}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ATTRACTIVE

attractive
}
\vspace*{\stretch{1}}
\begin{center}
ATTRACTIVE a. \textipa{[\textschwa \textprimstress tr\ae ktiv]}
\end{center}
1. 有吸引力的，引起注意的

She is an \textit{attractive} girl.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONSUMER

consumer
}
\vspace*{\stretch{1}}
\begin{center}
CONSUMER n. \textipa{[k\textschwa n\textprimstress sju\textlengthmark m\textschwa, k\textschwa n\textprimstress su\textlengthmark m\textschwa]}
\end{center}
1. 消费者，用户

The price increases were passed on by the firm to the \textit{consumer}.

2. 消耗者

The factory is a big coal \textit{consumer} in the region.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
APPROACH

approach
}
\vspace*{\stretch{1}}
\begin{center}
APPROACH v. n. \textipa{[\textschwa \textprimstress pr\textschwa ut\textesh]}
\end{center}
v. 1. 靠近，接近

Walk softly as you \textit{approach} the baby's crib.

n. 1. 接近

Our \textit{approach} drove away the wild animals.

n. 2. 途径

His best \textit{approach} to the great man lay through a mutual friend.

n. 3. 方式，方法，态度

Another member took a more cynical \textit{approach}.

\vspace*{\stretch{1}}
\end{flashcard}
