% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AVOID

avoid
}
\vspace*{\stretch{1}}
\begin{center}
AVOID vt. \textipa{[\textschwa \textprimstress v\textopeno id]}
\end{center}
1. 避免，避开

You should \textit{avoid} being late for your class.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ASSOCIATE

associate
}
\vspace*{\stretch{1}}
\begin{center}
ASSOCIATE vt. vi. \textipa{[\textschwa \textprimstress s\textschwa u\textesh ieit]} n. a. \textipa{[\textschwa \textprimstress s\textschwa u\textesh i\textschwa t]}
\end{center}
vt. 1. （在思想上）把...联系在一起；使联合，结合，使有联系

I can't \textit{associate} the two ideas.

She \textit{associated} herself with her father in banking.

vi. 1. (with)交往

They prefer to \textit{associate} with friends of their own age.

n. 1. 伙伴；a. 1. 副的

He was my close \textit{associate} at school.

\textit{associate} professor

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ARTIFICIAL

artificial
}
\vspace*{\stretch{1}}
\begin{center}
ARTIFICIAL a. \textipa{[\textsecstress \textscripta \textlengthmark ti\textprimstress fi\textesh \textschwa l]}
\end{center}
1. 人工的，人造的

natural flowers and \textit{artificial} ones

2. 非原地产的，人工栽培的

The ginseng is an \textit{artificial} plant in South China.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MANIPULATE

manipulate
}
\vspace*{\stretch{1}}
\begin{center}
MANIPULATE vt. \textipa{[m\textschwa \textprimstress nipjuleit]}
\end{center}
1. 操纵，控制

He \textit{manipulated} the sails like a sailor.

2. （熟练地）操作，使用

He told me in a confident voice that he knew how to \textit{manipulate} a computer.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PREDOMINANT

predominant
}
\vspace*{\stretch{1}}
\begin{center}
PREDOMINANT a. \textipa{[pri\textprimstress d\textopeno min\textschwa nt]}
\end{center}
1. 占主导地位的，显著的

Italian opera became absolutely \textit{predominant} at the end of the 17th century.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CREATION

creation
}
\vspace*{\stretch{1}}
\begin{center}
CREATION n. \textipa{[kri\textlengthmark \textprimstress ei\textesh \textschwa n]}
\end{center}
1. 创造，创建

The \textit{creation} of new playgrounds will benefit the local children.

2. 宇宙，天地万物

Man is the lord of \textit{creation}.

3. 创造的作品，（智力、想象力的）产物

Language is the most important mental \textit{creation} of man.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ANALOGY

analogy
}
\vspace*{\stretch{1}}
\begin{center}
ANALOGY n. \textipa{[\textschwa \textprimstress n\ae l\textschwa d\textyogh i]}
\end{center}
1. 比拟，类比

draw an \textit{analogy} between the human heart and a pump

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RANK

rank
}
\vspace*{\stretch{1}}
\begin{center}
RANK n. vi. vt. \textipa{[r\ae \ng k]}
\end{center}
n. 1. 军衔，职衔

He holds the \textit{rank} of colonel.

n. 2. 地位，社会阶层

He wasn't getting the salary to which he was entitled by \textit{rank} and seniority.

vi. 1. 列入，（在序列中）占特定等级

The cups were \textit{ranked} neatly on the shelf.

vt. 1. 把...分等，给...评定等级

They \textit{rand} vessel size by length or weight of the ship.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRINCIPLE

principle
}
\vspace*{\stretch{1}}
\begin{center}
PRINCIPLE n. \textipa{[\textprimstress prinsip\textschwa l]}
\end{center}
1. 原则，原理

You have to remember these \textit{principles} of geometry first.

2. 主义，信念

It is against my \textit{principles} to tell a lie.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
APPEAL

appeal
}
\vspace*{\stretch{1}}
\begin{center}
APPEAL vi. n. \textipa{[\textschwa \textprimstress pi\textlengthmark l]}
\end{center}
\normalsize vi. 1. 呼吁，恳求；申诉；(to)诉诸，求助

\footnotesize Politicians at all levels \textit{appealed} for calm.

\footnotesize He \textit{appealed} against the conviction.

\footnotesize When Mother said "No", my little sister would \textit{appeal} to Father.

\normalsize n. 1. 呼吁，要求；申诉；吸引力

\footnotesize The mayor launched an \textit{appeal} to the public to donate blood to the victims of the disaster.

\footnotesize The case is on \textit{appeal}, with the judge's order temporarily suspended pending a final ruling.

\footnotesize This kind of music hasn't much \textit{appeal} for me.

\vspace*{\stretch{1}}
\end{flashcard}
