% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INFLUENCE

influence
}
\vspace*{\stretch{1}}
\begin{center}
INFLUENCE n. vt. \textipa{[\textprimstress influ\textschwa ns]}
\end{center}
n. 1. 影响，感化力

Her \textit{influence} made me a better person.

n. 2. 势力，权势

He used his \textit{influence} to get his son a job.

vt. 1. 影响，感化

He was \textit{influenced} by a high-school biology teacher to take up the study of medicine.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPLEX

complex
}
\vspace*{\stretch{1}}
\begin{center}
COMPLEX n. \textipa{[\textprimstress k\textopeno mpleks]}
\end{center}
1. 情结

He has a \textit{complex} about his weight.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ESSENTIAL

essential
}
\vspace*{\stretch{1}}
\begin{center}
ESSENTIAL a. n. \textipa{[i\textprimstress sen\textesh \textschwa l]}
\end{center}
a. 1. 必要的，必不可少的

Discipline is \textit{essential} in an army.

a. 2. 本质的，基本的

an \textit{essential} difference

n. 1. [常 pl.]本质，要素，要点

Intensity is the first \textit{essential} in performance.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRESSURE

pressure
}
\vspace*{\stretch{1}}
\begin{center}
PRESSURE n. vt. \textipa{[\textprimstress pre\textesh \textschwa]}
\end{center}
n. 1. 压（力），压强

Lion's relentless \textit{pressure} counted for nothing as they went in at halftime 1-0 down.

n. 2. 强制，压迫

The sick man complained of a feeling of \textit{pressure} in his chest.

vt. 1. 对...施加压力（或影响），迫使，说服

My parents \textit{pressure} me into taking the examination.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EXPENSE

expense
}
\vspace*{\stretch{1}}
\begin{center}
EXPENSE n. \textipa{[ik\textprimstress spens]}
\end{center}
1. 价钱，花费

They fixed the sink themselves and saved the \textit{expense} of a plumber.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AMBIGUOUS

ambiguous
}
\vspace*{\stretch{1}}
\begin{center}
AMBIGUOUS a. \textipa{[\ae m\textprimstress bigju\textschwa s]}
\end{center}
1. 含糊不清的，不明确的

His answer was \textit{ambiguous}.

2. 引起歧义的，模棱两可的

Please avoid \textit{ambiguous} instructions.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INVARIABLY

invariably
}
\vspace*{\stretch{1}}
\begin{center}
INVARIABLY ad. \textipa{[in\textprimstress v\textepsilon \textschwa ri\textschwa bli]}
\end{center}
1. 不变地，始终如一地，总是

His intuition is \textit{invariably} correct.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPLEMENT

complement
}
\vspace*{\stretch{1}}
\begin{center}
COMPLEMENT vt. \textipa{[\textprimstress k\textopeno mpliment]} n. \textipa{[\textprimstress k\textopeno mplim\textschwa nt]}
\end{center}
vt. 1. 补足，补充

The TV networks and newspapers \textit{complement} each other and should not quarrel.

n. 1. 补充，互为补充的东西；编制名额，装备定额

Travel can be an excellent \textit{complement} to one's education.

The squadron was far under \textit{complement}.

n. 2. 补（足）语

a subject \textit{complement}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PETTY

petty
}
\vspace*{\stretch{1}}
\begin{center}
PETTY a. \textipa{[\textprimstress peti]}
\end{center}
1. 小的，琐碎的，不重要的

Don't bother the supervisor with such \textit{petty} matters.

2. 气量小的，心胸狭窄的

It was \textit{petty} of her not to accept the apology.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BEING

being
}
\vspace*{\stretch{1}}
\begin{center}
BEING n. \textipa{[\textprimstress bi\textlengthmark i\ng]}
\end{center}
1. 生物，人

He wanted to probe the asteroid belt for signs of intelligent alien \textit{beings}.

2. 存在

That was what she was for, that was her reason for \textit{being}.

\vspace*{\stretch{1}}
\end{flashcard}
