% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OBJECTIVE

objective
}
\vspace*{\stretch{1}}
\begin{center}
OBJECTIVE n. a. \textipa{[\textschwa b\textprimstress d\textyogh ektiv]}
\end{center}
n. 1. 目标，目的

Her \textit{objective} is to get a college education.

a. 1. 客观的，不带偏见的

The writer tried to be as \textit{objective} as possible in evaluating his latest work.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OBVIOUS

obvious
}
\vspace*{\stretch{1}}
\begin{center}
OBVIOUS a. \textipa{[\textprimstress \textopeno bvi\textschwa s]}
\end{center}
1. 显然的，明显的

It was \textit{obvious} that I knew very little about it.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MAGNETIC

magnetic
}
\vspace*{\stretch{1}}
\begin{center}
MAGNETIC a. \textipa{[m\ae g\textprimstress netik]}
\end{center}
1. 磁的，有磁性的

This iron has lost its \textit{magnetic} force.

2. 有吸引力的，有魅力的

Many film stars are popular because of their \textit{magnetic} personalities.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONSTRUCT

construct
}
\vspace*{\stretch{1}}
\begin{center}
CONSTRUCT vt. \textipa{[k\textschwa n\textprimstress str\textturnv kt]}
\end{center}
1. 建造，构筑

Eyewitness reports \textit{construct} a detailed description of the man.

2. 对...进行构思，造（句）

\textit{construct} the plot of a story

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ABSURD

absurd
}
\vspace*{\stretch{1}}
\begin{center}
ABSURD a. \textipa{[\textschwa b\textprimstress s\textschwa \textlengthmark d]}
\end{center}
1. 荒谬的，荒唐的

The idea that the number 13 brings bad luck is \textit{absurd}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTACT

intact
}
\vspace*{\stretch{1}}
\begin{center}
INTACT a. \textipa{[in\textprimstress t\ae kt]}
\end{center}
1. 完整无缺的，未经触动的，未受损伤的

The glasses remained \textit{intact} after being dropped.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MINIBUS

minibus
}
\vspace*{\stretch{1}}
\begin{center}
MINIBUS n. \textipa{[\textprimstress minib\textturnv s]}
\end{center}
1. 小型公共汽车

Some of the children living in the countryside go to school in a \textit{minibus}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
POTENTIAL

potential
}
\vspace*{\stretch{1}}
\begin{center}
POTENTIAL a. n. \textipa{[p\textschwa \textprimstress ten\textesh l]}
\end{center}
a. 1. 潜在的，可能的

That hole in the road is a \textit{potential} danger.

n. 1. 潜力，潜能

The \textit{potential} for coal production has been held back by the wage problem.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
NORTH

north
}
\vspace*{\stretch{1}}
\begin{center}
NORTH n. a. ad. \textipa{[n\textopeno \textlengthmark \texttheta]}
\end{center}
n. 1. 北（方），北部

The \textit{North} defeated the South in 1865.

a. 1. 北方的，北部的，来自北方的

A cold \textit{north} wind has begun to blow.

ad. 1. 向北方

They hurried \textit{north} to antiwar protests.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CANDIDATE

candidate
}
\vspace*{\stretch{1}}
\begin{center}
CANDIDATE n. \textipa{[\textprimstress k\ae ndideit]}
\end{center}
1. 候选人

There were three \textit{candidates} for the vacancy.

2. 投考者，申请求职者

There were six hundred \textit{candidates} for the entrance examination.

\vspace*{\stretch{1}}
\end{flashcard}
