% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GROWTH

growth
}
\vspace*{\stretch{1}}
\begin{center}
GROWTH n. \textipa{[gr\textschwa u\texttheta]}
\end{center}
1. 增长，增加

the world population \textit{growth}

2. 生长，发展

They stunt plant \textit{growth} and reduce yields.

3. 生长物

Each year the seaweed \textit{growth} returns and has to be cleared.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SWITCH

switch
}
\vspace*{\stretch{1}}
\begin{center}
SWITCH n. v. \textipa{[swit\textesh]}
\end{center}
n. 1. 开关，电闸

I couldn't find the \textit{switch} in the dark.

n. 2. 转变，改变

When did you make the \textit{switch} from coal to gas in this house?

v. 1. 转变，改变，转换

After \textit{switching} direction several times I found myself in front of the post office.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RELY

rely
}
\vspace*{\stretch{1}}
\begin{center}
RELY vi. \textipa{[ri\textprimstress lai]}
\end{center}
1. (on, upon)依靠，依赖

He was \textit{relying} upon a broken reed.

2. 信赖，对...有信心

He is the man who we can \textit{rely} on.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONFIDENTIAL

confidential
}
\vspace*{\stretch{1}}
\begin{center}
CONFIDENTIAL a. \textipa{[\textsecstress k\textopeno nfi\textprimstress den\textesh \textschwa l]}
\end{center}
1. 秘密的，机密的

This is completely \textit{confidential}.

2. 表示信任（或亲密）的

He spoke in a \textit{confidential} tone.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEDICATE

dedicate
}
\vspace*{\stretch{1}}
\begin{center}
DEDICATE vt. \textipa{[\textprimstress dedikeit]}
\end{center}
1. (to)（把自己、一生等）献给，把（时间、精力等）用于

The doctor \textit{dedicated} himself to finding a cure.

2. （题词）将（著作等）献给

A monument was \textit{dedicated} to the memory of the soldiers who had died there.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VICINITY

vicinity
}
\vspace*{\stretch{1}}
\begin{center}
VICINITY n. \textipa{[vi\textprimstress sin\textschwa ti]}
\end{center}
1. 周围地区，邻近地区

the inhabitants of the \textit{vicinity}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ASPIRATION

aspiration
}
\vspace*{\stretch{1}}
\begin{center}
ASPIRATION n. \textipa{[\textsecstress \ae sp\textschwa \textprimstress rei\textesh \textschwa n]}
\end{center}
1. 强烈的愿望，志向，抱负

He has \textit{aspirations} to greatness.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
THREATEN

threaten
}
\vspace*{\stretch{1}}
\begin{center}
THREATEN vt. \textipa{[\textprimstress \texttheta retn]}
\end{center}
1. 威胁，扬言要

He \textit{threatened} me with a gun.

2. 预示，是...的征兆

Dark skies \textit{threaten} rain.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STATEMENT

statement
}
\vspace*{\stretch{1}}
\begin{center}
STATEMENT n. \textipa{[\textprimstress steitm\textschwa nt]}
\end{center}
1. 声明，陈述，说法

I could not deny the truth of this \textit{statement}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
KID

kid
}
\vspace*{\stretch{1}}
\begin{center}
KID n. v. \textipa{[kid]}
\end{center}
n. 1. 小孩，年轻人

Many \textit{kids} were playing in the park.

v. 1. 戏弄，（与...）开玩笑

Are you \textit{kidding}?

\vspace*{\stretch{1}}
\end{flashcard}
