% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PERSPECTIVE

perspective
}
\vspace*{\stretch{1}}
\begin{center}
PERSPECTIVE n. \textipa{[p\textschwa \textprimstress spektiv]}
\end{center}
1. 视角，观点，想法

He tends to view most issues from a religious \textit{perspective}.

2. 远景，景观

A snow \textit{perspective} spread before us.

3. 透视画法，透视图

a lesson in drawing class on \textit{perspective}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMMISSION

commission
}
\vspace*{\stretch{1}}
\begin{center}
COMMISSION n. vt. \textipa{[k\textschwa \textprimstress mi\textesh n]}
\end{center}
n. 1. 授权，委托；佣金，回扣；委员会

The \textit{commission} for the new theatre was given to a well-known architect.

She gets a \textit{commission} of 10 percent on all the sales she makes.

He was a member of the \textit{commission} investigating crimes.

vt. 1. 委任，委托

He was \textit{commissioned} a general.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OFFENSIVE

offensive
}
\vspace*{\stretch{1}}
\begin{center}
OFFENSIVE a. n. \textipa{[\textschwa \textprimstress fensiv]}
\end{center}
a. 1. 冒犯的，无礼的；使人不快的

The odor from the garbage is \textit{offensive}.

n. 1. 进攻，攻势

The troops are on the \textit{offensive}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RECTIFY

rectify
}
\vspace*{\stretch{1}}
\begin{center}
RECTIFY vt. \textipa{[\textprimstress rektifai]}
\end{center}
1. 纠正，修复

It will take days on \textit{rectify} the damage.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TERMINATE

terminate
}
\vspace*{\stretch{1}}
\begin{center}
TERMINATE v. \textipa{[\textprimstress t\textschwa \textlengthmark mineit]}
\end{center}
1. 停止，（使）终止

The meeting \textit{terminated} at 5 p.m.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRESCRIPTION

prescription
}
\vspace*{\stretch{1}}
\begin{center}
PRESCRIPTION n. \textipa{[pris\textprimstress krip\textesh \textschwa n]}
\end{center}
1. 处方，药方

give a \textit{prescription} for an ailment

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RANDOM

random
}
\vspace*{\stretch{1}}
\begin{center}
RANDOM a. \textipa{[\textprimstress r\ae nd\textschwa m]}
\end{center}
1. 任意的，随机的

The way the books were arranged seemed completely \textit{random}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEPRESSION

depression
}
\vspace*{\stretch{1}}
\begin{center}
DEPRESSION n. \textipa{[di\textprimstress pre\textesh \textschwa n]}
\end{center}
1. 抑郁，沮丧

He is suffering from a \textit{depression} and has to be hospitalized.

2. 不景气，萧条（期）

Many people still remember the acute \textit{depression} of the 1930's.

3. 凹地，凹陷

Water fills the \textit{depression} in the ground.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CAPACITY

capacity
}
\vspace*{\stretch{1}}
\begin{center}
CAPACITY n. \textipa{[k\textschwa \textprimstress p\ae s\textschwa ti]}
\end{center}
1. 容量，容积

This hotel has a large \textit{capacity}.

2. 才能，能力

They always think of military power in terms of potential \textit{capacity} for action.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RESERVE

reserve
}
\vspace*{\stretch{1}}
\begin{center}
RESERVE vt. n. \textipa{[ri\textprimstress z\textschwa \textlengthmark v]}
\end{center}
vt. 1. 保留，留存；预定

We'll \textit{reserve} the ticket for you till tomorrow noon.

I have \textit{reserved} two tickets for tonight's show.

n. 1. 储备（物），后备人员

The division went into \textit{reserve} after several weeks of hard fighting.

n. 2. 储量，藏量

I feel quite rested already, but I know that I need a little \textit{reserve}.

\vspace*{\stretch{1}}
\end{flashcard}
