% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PURCHASE

purchase
}
\vspace*{\stretch{1}}
\begin{center}
PURCHASE vt. n. \textipa{[\textprimstress p\textschwa \textlengthmark t\textesh \textschwa s]}
\end{center}
vt. 1. 买，购买

They have \textit{purchased} 30 percent of the shares of the company.

n. 1. 购买，购买的物品

Mother gave me some money for the \textit{purchase} of my school books.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CHALLENGE

challenge
}
\vspace*{\stretch{1}}
\begin{center}
CHALLENGE n. vt. \textipa{[\textprimstress t\textesh \ae lind\textyogh]}
\end{center}
n. 1. 挑战

He accepted his friend's \textit{challenge} to swim across the river.

vt. 1. 向...挑战

Our school \textit{challenged} the local champion team to a football match.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONVEY

convey
}
\vspace*{\stretch{1}}
\begin{center}
CONVEY vt. \textipa{[k\textschwa n\textprimstress vei]}
\end{center}
1. 传送，传达

A wire \textit{conveys} an electric current.

2. 运送，输送

A taxi \textit{conveyed} us to the train station.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ENTITY

entity
}
\vspace*{\stretch{1}}
\begin{center}
ENTITY n. \textipa{[\textprimstress entiti]}
\end{center}
1. 实体，独立存在体，实际存在物

The Radley Place was inhabited by an unknown \textit{entity}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PATENT

patent
}
\vspace*{\stretch{1}}
\begin{center}
PATENT n. vt. \textipa{[\textprimstress peit\textschwa nt, \textprimstress p\ae t\textschwa nt]}
\end{center}
n. 1. 专利，专利权

\textit{Patents} have been running out on these drugs.

vt. 1. 得到...的专利权

The company had \textit{patented} many new inventions.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SILICON

silicon
}
\vspace*{\stretch{1}}
\begin{center}
SILICON n. \textipa{[\textprimstress silik\textschwa n]}
\end{center}
1. 硅

A \textit{silicon} chip is used in computers, calculators and other electronic machines.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TENANT

tenant
}
\vspace*{\stretch{1}}
\begin{center}
TENANT n. \textipa{[\textprimstress ten\textschwa nt]}
\end{center}
1. 房客，佃户

This is Mr. Smith, a new \textit{tenant}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUFFICIENT

sufficient
}
\vspace*{\stretch{1}}
\begin{center}
SUFFICIENT a. \textipa{[s\textschwa \textprimstress fi\textesh \textschwa nt]}
\end{center}
1. 足够的，充分的

He has impudence \textit{sufficient} for anything.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SHIFT

shift
}
\vspace*{\stretch{1}}
\begin{center}
SHIFT v. n. \textipa{[\textesh ift]}
\end{center}
v. 1. 移动，转移

He \textit{shifted} the chair closer to the bed.

v. 2. 改变，转变

The candidate was constantly \textit{shifting} his position on the issues.

n. 1. 转换，转变

A \textit{shift} in the wind brought rain.

n. 2. （轮或换）班

I was on the night \textit{shift} that day.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BOMB

bomb
}
\vspace*{\stretch{1}}
\begin{center}
BOMB n. vi. \textipa{[b\textopeno m]}
\end{center}
n. 1. 炸弹

An atomic \textit{bomb} was dropped on Hiroshima in 1945.

vi. 1. 大败，惨败

They \textit{bombed} in the movies.

\vspace*{\stretch{1}}
\end{flashcard}
