% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OBTAIN

obtain
}
\vspace*{\stretch{1}}
\begin{center}
OBTAIN vt. \textipa{[\textschwa b\textprimstress tein]}
\end{center}
1. 获得，得到

She \textit{obtained} her degree in 1951.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INSTANCE

instance
}
\vspace*{\stretch{1}}
\begin{center}
INSTANCE n. \textipa{[\textprimstress inst\textschwa ns]}
\end{center}
1. 例子，实例，事例

I'll give you an \textit{instance} of it.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INNER

inner
}
\vspace*{\stretch{1}}
\begin{center}
INNER a. \textipa{[\textprimstress in\textschwa]}
\end{center}
1. 内部的，里面的；内心的

\textit{inner} feelings

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OVERWHELM

overwhelm
}
\vspace*{\stretch{1}}
\begin{center}
OVERWHELM vt. \textipa{[\textsecstress \textschwa uv\textschwa \textprimstress welm]}
\end{center}
1. 使不知所措

The horror of it all had \textit{overwhelmed} me.

2. 征服，制服

He took 45\% of the ballots and \textit{overwhelmed} his two main rivals.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CORPORATE

corporate
}
\vspace*{\stretch{1}}
\begin{center}
CORPORATE a. \textipa{[\textprimstress k\textopeno \textlengthmark p\textschwa rit]}
\end{center}
1. （结成）社团的，（法人）团体的，公司的

These are \textit{corporate} assets.

2. 全体的，共同的

The success was due not to one man but to \textit{corporate} effort.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
KIN

kin
}
\vspace*{\stretch{1}}
\begin{center}
KIN n. \textipa{[kin]}
\end{center}
1. [总称]亲属，家属

All our \textit{kin} got together.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MUDDY

muddy
}
\vspace*{\stretch{1}}
\begin{center}
MUDDY a. vt. \textipa{[\textprimstress m\textturnv di]}
\end{center}
a. 1. 泥泞的，沾满烂泥的

The boy's pants were \textit{muddy}.

a. 2. （光，色泽 ）灰暗的，暗淡的

The room has a \textit{muddy} colour.

vt. 1. 使（形势、争端等）显得扑朔迷离

The spokesman's explanation \textit{muddied} the mess further.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONDUCT

conduct
}
\vspace*{\stretch{1}}
\begin{center}
CONDUCT vt. \textipa{[k\textschwa n\textprimstress d\textturnv kt]}
\end{center}
1. 进行，管理

He \textit{conducted} the business very successfully.

2. 指挥，引导

The usher \textit{conducted} me to my seat.

3. 输送，传导（热、电等）

Copper \textit{conducts} electricity better than other materials.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
NOTION

notion
}
\vspace*{\stretch{1}}
\begin{center}
NOTION n. \textipa{[\textprimstress n\textschwa u\textesh \textschwa n]}
\end{center}
1. 概念，感知

Her \textit{notion} of rural life is a lot of sunshine and fun.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REPRESENT

represent
}
\vspace*{\stretch{1}}
\begin{center}
REPRESENT vt. \textipa{[\textsecstress repri\textprimstress zent]}
\end{center}
1. 作...代表（代理）

An ambassador \textit{represents} his government in a foreign country.

2. 表示，象征

The blue lines on the map \textit{represent} rivers.

3. 描绘，表现

He \textit{represented} her as a love-goddess.

\vspace*{\stretch{1}}
\end{flashcard}
