% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INVOLVE

involve
}
\vspace*{\stretch{1}}
\begin{center}
INVOLVE vt. \textipa{[in\textprimstress v\textopeno lv]}
\end{center}
1. 使卷入，使参与

He was \textit{involved} in a howling dancing crowd.

2. 牵涉

The investigation \textit{involved} many innocent people.

3. 包含，含有

Swimming necessarily \textit{involves} long hours of strenuous training.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CELL

cell
}
\vspace*{\stretch{1}}
\begin{center}
CELL n. \textipa{[sel]}
\end{center}
1. 细胞

\textit{cell} division

2. 小牢房，单人小室

The prisoner was put in a \textit{cell}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ASCEND

ascend
}
\vspace*{\stretch{1}}
\begin{center}
ASCEND vi. vt. \textipa{[\textschwa \textprimstress send]}
\end{center}
vi. 1. 渐渐上升，升高

The airplane \textit{ascended} into the cloud.

vt. 1. 攀登，登上

We \textit{ascended} Mt. Tai.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DENIAL

denial
}
\vspace*{\stretch{1}}
\begin{center}
DENIAL n. \textipa{[di\textprimstress nai\textschwa l]}
\end{center}
1. 否认

He met the charge with a flat \textit{denial}.

2. 拒绝，拒绝给予

the \textit{denial} of visas

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRECEDENT

precedent
}
\vspace*{\stretch{1}}
\begin{center}
PRECEDENT n. \textipa{[\textprimstress presid\textschwa nt]}
\end{center}
1. 先例，范例，判例

There is no \textit{precedent} for such a case.

2. 惯例

It is against \textit{precedents}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
HIGHWAY

highway
}
\vspace*{\stretch{1}}
\begin{center}
HIGHWAY n. \textipa{[\textprimstress haiwei]}
\end{center}
1. 公路，交通要道

The river was the only \textit{highway} for commerce.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PACE

pace
}
\vspace*{\stretch{1}}
\begin{center}
PACE n. vi. \textipa{[peis]}
\end{center}
n. 1. 步速，速度，节奏

They traveled at a snail's \textit{pace}.

n. 2. 一步

She finished only a few \textit{paces} behind the winner.

vi. 1. 踱步

The lion \textit{paced} up and down restlessly.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EVAPORATE

evaporate
}
\vspace*{\stretch{1}}
\begin{center}
EVAPORATE v. \textipa{[i\textprimstress v\ae p\textschwa reit]}
\end{center}
1. 蒸发，挥发；消失，不复存在

Heat \textit{evaporates} water.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
WRETCHED

wretched
}
\vspace*{\stretch{1}}
\begin{center}
WRETCHED a. \textipa{[\textprimstress ret\textesh id]}
\end{center}
1. 不幸的，悲惨的

The widow was leading a \textit{wretched} life.

2. 令人苦恼的，讨厌的

Neglected by the authorities for decades, the village is now in a \textit{wretched} condition.

3. 拙劣的

He gave a \textit{wretched} excuse for coming late.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OWL

owl
}
\vspace*{\stretch{1}}
\begin{center}
OWL n. \textipa{[aul]}
\end{center}
1. 猫头鹰

He was naturally a night \textit{owl}.

\vspace*{\stretch{1}}
\end{flashcard}
