% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ADVANTAGE

advantage
}
\vspace*{\stretch{1}}
\begin{center}
ADVANTAGE n. \textipa{[\textschwa d\textprimstress v\textscripta \textlengthmark ntid\textyogh]}
\end{center}
1. 优点，有利条件，有利因素

The only \textit{advantage} of the plan is its simplicity.

2. 利益，好处

They are seeking some kind of commercial \textit{advantage}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPETITIVE

competitive
}
\vspace*{\stretch{1}}
\begin{center}
COMPETITIVE a. \textipa{[k\textschwa m\textprimstress petitiv]}
\end{center}
1. 竞争的

He took the \textit{competitive} examination for the job of postal clerk.

2. 好竞争的

He is not at all \textit{competitive}.

3. （价格等）有竞争力的

Their exports are becoming less price \textit{competitive}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
REPLACE

replace
}
\vspace*{\stretch{1}}
\begin{center}
REPLACE v. \textipa{[ri\textprimstress pleis]}
\end{center}
1. 替换，取代

The calculator is rapidly \textit{replacing} the abacus.

2. 把...放回原处

Please \textit{replace} the cards in their correct positions in the files.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMPORT

import
}
\vspace*{\stretch{1}}
\begin{center}
IMPORT n. \textipa{[\textprimstress imp\textopeno \textlengthmark t]}
\end{center}
1. 进口，输入

The \textit{import} of crude oil increased in June.

2. 意义，重要性

a matter of great \textit{import}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CUMULATIVE

cumulative
}
\vspace*{\stretch{1}}
\begin{center}
CUMULATIVE a. \textipa{[\textprimstress kju\textlengthmark mjul\textschwa tiv]}
\end{center}
1. 积累的，渐增的

The \textit{cumulative} effects of many illnesses made him very weak.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
NOTABLE

notable
}
\vspace*{\stretch{1}}
\begin{center}
NOTABLE a. n. \textipa{[\textprimstress n\textschwa ut\textschwa bl]}
\end{center}
a. 1. 值得注意的，显著的

His lecture was a \textit{notable} success.

a. 2. 有相当分量的

\textit{notable} quantity

n. 1. 显要人物

Many \textit{notables} came to the reception at the White House.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BARREN

barren
}
\vspace*{\stretch{1}}
\begin{center}
BARREN a. \textipa{[\textprimstress b\ae r\textschwa n]}
\end{center}
1. （土地等）贫瘠的，荒芜的

a \textit{barren} hillside

2. 不（生）育的，不结果实的

a \textit{barren} mating

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
APPROPRIATE

appropriate
}
\vspace*{\stretch{1}}
\begin{center}
APPROPRIATE a. \textipa{[\textschwa \textprimstress pr\textschwa upriit]}
\end{center}
1. 适当的，合适的，可应用的

It's \textit{appropriate} that he should get the post.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DETECTIVE

detective
}
\vspace*{\stretch{1}}
\begin{center}
DETECTIVE n. \textipa{[di\textprimstress tektiv]}
\end{center}
1. 侦探，私人侦探

He employed a private \textit{detective}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SATELLITE

satellite
}
\vspace*{\stretch{1}}
\begin{center}
SATELLITE n. \textipa{[\textprimstress s\ae t\textschwa lait]}
\end{center}
1. （人造）卫星

The broadcast came from America by \textit{satellite}.

\vspace*{\stretch{1}}
\end{flashcard}
