% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TEND

tend
}
\vspace*{\stretch{1}}
\begin{center}
TEND vi. \textipa{[tend]}
\end{center}
1. 易于，往往会

Plants \textit{tend} to die in hot weather if you don't water them.

2. 趋向，倾向

Interest rates are \textit{tending} upwards/downwards.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LEGAL

legal
}
\vspace*{\stretch{1}}
\begin{center}
LEGAL a. \textipa{[\textprimstress li\textlengthmark g\textschwa l]}
\end{center}
1. 法律（上）的

You'd better get a \textit{legal} adviser.

2. 合法的，法定的

Punishment by hanging is \textit{legal} in many countries.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEFINE

define
}
\vspace*{\stretch{1}}
\begin{center}
DEFINE vt. \textipa{[di\textprimstress fain]}
\end{center}
1. 给...下定义，解释

People \textit{define} him as a genius.

2. 限定，规定

The boundary between the two nations is \textit{defined} by treaty.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PERFORMANCE

performance
}
\vspace*{\stretch{1}}
\begin{center}
PERFORMANCE n. \textipa{[p\textschwa \textprimstress f\textopeno \textlengthmark m\textschwa ns]}
\end{center}
1. 演出，表演

His first \textit{performance} in China will be given tonight.

2. 履行，执行

He was faithful in the \textit{performance} of his duties.

3. 工作，情况，表现

We must watch the \textit{performance} of the stock market.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
APPLY

apply
}
\vspace*{\stretch{1}}
\begin{center}
APPLY vi. vt. \textipa{[\textschwa \textprimstress plai]}
\end{center}
vi. 1. 申请，请求

You may \textit{apply} in person or by letter.

vt. 1. 使用，运用，实施

Scientific discoveries are often \textit{applied} to industrial production methods.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUBURB

suburb
}
\vspace*{\stretch{1}}
\begin{center}
SUBURB n. \textipa{[\textprimstress s\textturnv b\textschwa \textlengthmark b]}
\end{center}
1. 市郊，郊区

The kidnapping took place in a northern \textit{suburb} of Rome.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ADHERE

adhere
}
\vspace*{\stretch{1}}
\begin{center}
ADHERE vi. \textipa{[\textschwa d\textprimstress hi\textschwa]}
\end{center}
1. (to)黏附，附着

Mud \textit{adhered} to his shoes.

2. 遵守，坚持

That government \textit{adhered} to its original plan in spite of the resistance.

3. 追随，支持

\textit{adhere} to a leader faithfully

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PROBABILITY

probability
}
\vspace*{\stretch{1}}
\begin{center}
PROBABILITY n. \textipa{[\textsecstress pr\textopeno b\textschwa \textprimstress bil\textschwa ti]}
\end{center}
1. 可能性，可能发生的事

There is no/little/not much \textit{probability} of his succeeding/that he will succeed.

2. 概率

The cluster bomb has a high kill \textit{probability} against a range of small hard and soft targets.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MORALITY

morality
}
\vspace*{\stretch{1}}
\begin{center}
MORALITY n. \textipa{[m\textschwa \textprimstress r\ae l\textschwa ti]}
\end{center}
1. 道德，（行为等的）道德性

We talked about the \textit{morality} of fox-hunting.

2. 德行，品行

We need their \textit{morality} and wisdom.

3. 道德规范，道德观

Victorian \textit{morality}

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CHRONIC

chronic
}
\vspace*{\stretch{1}}
\begin{center}
CHRONIC a. \textipa{[\textprimstress kr\textopeno nik]}
\end{center}
1. （疾病）慢性的

Some acute illnesses may become \textit{chronic}.

2. 积习难改的

a \textit{chronic} grumbler

3. 严重的，坏的

Oh, that theatre's \textit{chronic}!

\vspace*{\stretch{1}}
\end{flashcard}
