% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
USER

user
}
\vspace*{\stretch{1}}
\begin{center}
USER n. \textipa{[\textprimstress ju\textlengthmark z\textschwa]}
\end{center}
1. 用户，使用者

the biggest \textit{user} of oil

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FINANCE

finance
}
\vspace*{\stretch{1}}
\begin{center}
FINANCE n. v. \textipa{[fai\textprimstress n\ae ns]}
\end{center}
n. 1. 财源，资金

They multiplied their \textit{finances} by speculating in the stock market.

v. 1. （为...）筹措资金

The campaign was \textit{financed} mainly through voluntary contributions.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMPULSE

impulse
}
\vspace*{\stretch{1}}
\begin{center}
IMPULSE n. \textipa{[\textprimstress imp\textturnv ls]}
\end{center}
1. 冲动，突然的欲望

He is ruled by his \textit{impulses}.

2. 脉冲

A remote control works by electric \textit{impulse}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEADLY

deadly
}
\vspace*{\stretch{1}}
\begin{center}
DEADLY a. ad. \textipa{[\textprimstress dedli]}
\end{center}
a. 1. 致死的，致命的

a \textit{deadly} poison/disease/blow

a. 2. 极度的，十足的

\textit{deadly} dullness

ad. 1. 非常，极度地

The old man's face was \textit{deadly} pale at that time.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LITTER

litter
}
\vspace*{\stretch{1}}
\begin{center}
LITTER n. vt. \textipa{[\textprimstress lit\textschwa]}
\end{center}
n. 1. 废弃物，被胡乱扔掉的东西

There were piles of \textit{litter} on the street.

n. 2. （一堆）杂乱的东西

A \textit{litter} of cocaine bags was found in the room.

vt. 1. 乱扔东西于

The children \textit{littered} the garden with cans and bottles.

vt. 2. 使充满

These books are \textit{littered} with miraculous stories.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPLAINT

complaint
}
\vspace*{\stretch{1}}
\begin{center}
COMPLAINT n. \textipa{[k\textschwa m\textprimstress pleint]}
\end{center}
1. 抱怨，诉苦

Our \textit{complaints} fell on deaf ears.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MEDIA

media
}
\vspace*{\stretch{1}}
\begin{center}
MEDIA n. \textipa{[\textprimstress mi\textlengthmark di\textschwa]}
\end{center}
1. 新闻媒介，传播媒介

The \textit{media} control the news.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STIMULUS

stimulus
}
\vspace*{\stretch{1}}
\begin{center}
STIMULUS n. \textipa{[\textprimstress stimjul\textschwa s]}
\end{center}
1. 促进（因素）

Her words of praise were a \textit{stimulus} to work harder.

2. 刺激（物）

Reduced tariffs were a \textit{stimulus} to foreign trade.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MINIMIZE/-ISE

minimize/-ise
}
\vspace*{\stretch{1}}
\begin{center}
MINIMIZE/-ISE v. \textipa{[\textprimstress minimaiz]}
\end{center}
1. 使减少（或缩小）到最低限度

He'd made a serious mistake, and it was no use trying to \textit{minimize} its seriousness.

2. 极力贬低，对...做最低估计

She \textit{minimized} the value of his contribution to her research.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IGNITE

ignite
}
\vspace*{\stretch{1}}
\begin{center}
IGNITE vt. vi. \textipa{[ig\textprimstress nait]}
\end{center}
vt. 1. 点燃

Fuel is \textit{ignited} by the spark plug.

vt. 2. 激起

\textit{ignite} a new round of inflation

vi. 1. 着火

Gasoline \textit{ignites} easily.

\vspace*{\stretch{1}}
\end{flashcard}
