% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RESOURCE

resource
}
\vspace*{\stretch{1}}
\begin{center}
RESOURCE n. \textipa{[ri\textprimstress s\textopeno \textlengthmark s]}
\end{center}
1. 资源

Oil is Kuwait's most important \textit{resource}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
VEHICLE

vehicle
}
\vspace*{\stretch{1}}
\begin{center}
VEHICLE n. \textipa{[\textprimstress vi\textlengthmark ikl]}
\end{center}
1. 交通工具，车辆

strategic nuclear delivery \textit{vehicles}

2. 传播媒介，工具，手段

Air is the \textit{vehicle} of sound.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GLOBAL

global
}
\vspace*{\stretch{1}}
\begin{center}
GLOBAL a. \textipa{[\textprimstress gl\textschwa ub\textschwa l]}
\end{center}
1. 全球的，全世界的

He gave a fairly accurate forecast of what might be expected to happen if another \textit{global} war broke out.

2. 总的，完整的

A \textit{global} picture can be obtained from...

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INDUSTRIAL

industrial
}
\vspace*{\stretch{1}}
\begin{center}
INDUSTRIAL a. \textipa{[in\textprimstress d\textturnv stri\textschwa l]}
\end{center}
1. 工业的，产业的

Many European countries are developed \textit{industrial} nations.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DRAMATIC

dramatic
}
\vspace*{\stretch{1}}
\begin{center}
DRAMATIC a. \textipa{[dr\textschwa \textprimstress m\ae tik]}
\end{center}
1. 戏剧性的

She tends to be very \textit{dramatic} about everything.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MANAGEMENT

management
}
\vspace*{\stretch{1}}
\begin{center}
MANAGEMENT n. \textipa{[\textprimstress m\ae nid\textyogh m\textschwa nt]}
\end{center}
1. 管理，经营，处理

A business can't do well without good \textit{management}.

2. 管理部门，管理人员

The company is under new \textit{management}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DEPRIVE

deprive
}
\vspace*{\stretch{1}}
\begin{center}
DEPRIVE vt. \textipa{[di\textprimstress praiv]}
\end{center}
1. (of)剥夺，使丧失

He was \textit{deprived} of his sight by the accident.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TRANSACTION

transaction
}
\vspace*{\stretch{1}}
\begin{center}
TRANSACTION n. \textipa{[tr\ae n\textprimstress z\ae k\textesh \textschwa n]}
\end{center}
1. 交易，业务

That was quite a profitable \textit{transaction}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONFORM

conform
}
\vspace*{\stretch{1}}
\begin{center}
CONFORM v. \textipa{[k\textschwa n\textprimstress f\textopeno \textlengthmark m]}
\end{center}
1. （使）顺从

We must \textit{conform} ourselves to the customs of society.

2. (to, with)遵照，适应

You should \textit{conform} to the rules of this school.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUPERIORITY

superiority
}
\vspace*{\stretch{1}}
\begin{center}
SUPERIORITY n. \textipa{[sju(\textlengthmark)\textsecstress pi\textschwa ri\textprimstress \textopeno r\textschwa ti]}
\end{center}
1. 优越（性），优等

Their vast \textit{superiority} in speed would be easily outweighed by the extortionate running costs.

\vspace*{\stretch{1}}
\end{flashcard}
