% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SCREEN

screen
}
\vspace*{\stretch{1}}
\begin{center}
SCREEN n. vt. \textipa{[skri\textlengthmark n]}
\end{center}
n. 1. 屏幕，银幕；屏风，帘，窗纱

I saw her on the TV \textit{screen}.

The bed was hidden by a \textit{screen}.

vt. 1. 掩蔽，遮蔽

She \textit{screened} her face from the fire with a mask.

vt. 2. 放映（电影），播放（电视节目）；审查

They tried to prevent the programme being \textit{screened}.

The Secret Service \textit{screens} several hundred people every week.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONVENTIONAL

conventional
}
\vspace*{\stretch{1}}
\begin{center}
CONVENTIONAL a. \textipa{[k\textschwa n\textprimstress ven\textesh \textschwa nl]}
\end{center}
1. 普通的，习惯的，常规的

It is \textit{conventional} to remark that any mistakes this book may contain are mine.

2. 符合习俗的，因循守旧的

He's not very \textit{conventional} in his behaviour.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OPTION

option
}
\vspace*{\stretch{1}}
\begin{center}
OPTION a. \textipa{[\textprimstress \textopeno p\textesh \textschwa n]}
\end{center}
1. 选择

It is at your \textit{option} to take it or leave it.

2. 选择权，选择自由

Every voter should exercise his \textit{option}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EXISTENCE

existence
}
\vspace*{\stretch{1}}
\begin{center}
EXISTENCE n. \textipa{[ig\textprimstress zist\textschwa ns]}
\end{center}
1. 存在

That company came into \textit{existence} / was brought into \textit{existence} in 1971.

2. 生存，生活（方式）

They were working hard for a better \textit{existence}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DESTRUCTION

destruction
}
\vspace*{\stretch{1}}
\begin{center}
DESTRUCTION n. \textipa{[di\textprimstress str\textturnv k\textesh \textschwa n]}
\end{center}
1. 破坏，毁坏，消灭

My house escaped \textit{destruction}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INGENIOUS

ingenious
}
\vspace*{\stretch{1}}
\begin{center}
INGENIOUS a. \textipa{[in\textprimstress d\textyogh i\textlengthmark nj\textschwa s]}
\end{center}
1. （人、头脑）灵巧的，善于创造发明的，足智多谋的

The chiefs were \textit{ingenious} at finding reasons not to move.

2. （机器等）制作精巧的，（方法等）巧妙的

It took a lot of imagination to come up with such \textit{ingenious} plan.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACCESSORY

accessory
}
\vspace*{\stretch{1}}
\begin{center}
ACCESSORY n. \textipa{[\textschwa k\textprimstress ses\textschwa ri]}
\end{center}
1. 附件，配件

A cigar-lighter is an \textit{accessory} to a car.

2. [常 pl.]（妇女的）装饰品（如手提包等）

I frequently change \textit{accessories} in my room.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMITATION

imitation
}
\vspace*{\stretch{1}}
\begin{center}
IMITATION n. a. \textipa{[\textsecstress imi\textprimstress tei\textesh \textschwa n]}
\end{center}
n. 1. 仿制，赝品

Beware of bogus \textit{imitations}.

n. 2. 模仿

We learn many things by \textit{imitation}.

a. 1. 人造的，仿制的，伪造的

an \textit{imitation} leather suitcase

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
GRIEVE

grieve
}
\vspace*{\stretch{1}}
\begin{center}
GRIEVE vi. vt. \textipa{[gri\textlengthmark v]}
\end{center}
vi. 1. (for, over)感到悲痛，伤心

The little girl \textit{grieved} over her kitten's death.

vt. 1. 使伤心，为...而伤心

Her behaviour \textit{grieved} her parents.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RISK

risk
}
\vspace*{\stretch{1}}
\begin{center}
RISK vt. n. \textipa{[risk]}
\end{center}
vt. 1. 冒...的危险

They were willing to \textit{risk} losing their jobs.

n. 1. 冒险，风险

I sank to my knees to reduce the \textit{risk} of detection.

\vspace*{\stretch{1}}
\end{flashcard}
