% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ATTACH

attach
}
\vspace*{\stretch{1}}
\begin{center}
ATTACH vt. \textipa{[\textschwa \textprimstress t\ae t\textesh]}
\end{center}
1. 系，贴，连接

I \textit{attached} a wire (to the radio).

2. 使依恋

He was strongly \textit{attached} to his home.

3. 认为有（重要性，责任等）

Different people \textit{attach} different meanings to words.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LARGELY

largely
}
\vspace*{\stretch{1}}
\begin{center}
LARGELY ad. \textipa{[\textprimstress l\textscripta \textlengthmark d\textyogh li]}
\end{center}
1. 大部分，主要地

His success is \textit{largely} due to luck.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
BLUNDER

blunder
}
\vspace*{\stretch{1}}
\begin{center}
BLUNDER vi. n. \textipa{[\textprimstress bl\textturnv nd\textschwa]}
\end{center}
vi. 1. （因无知、粗心等而）犯大错误

She \textit{blundered} in not packing a raincoat for her trip to England.

vi. 2. 踉踉跄跄地走

He \textit{blundered} out of the booth.

n. 1. 大错

His chief \textit{blunder} is his misconception of Kann.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IRRITATE

irritate
}
\vspace*{\stretch{1}}
\begin{center}
IRRITATE vt. \textipa{[\textprimstress iriteit]}
\end{center}
1. 使恼怒，使烦躁

be \textit{irritated} by sb.'s insolence

2. 使过敏，使难受，使疼痛

Sunburn \textit{irritates} the skin.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LIKELIHOOD

likelihood
}
\vspace*{\stretch{1}}
\begin{center}
LIKELIHOOD n. \textipa{[\textprimstress laiklihud]}
\end{center}
1. 可能，可能性

Is there any \textit{likelihood} of his coming?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRESUMABLY

presumably
}
\vspace*{\stretch{1}}
\begin{center}
PRESUMABLY ad. \textipa{[pri\textprimstress zju\textlengthmark m\textschwa bli]}
\end{center}
1. 大概，可能，据推测

\textit{Presumably} he won't see you, if you're leaving tomorrow.

2. 效果不错的

He spoke \textit{effective} Chinese.

3. 有战斗力的

The fort was held by about 100 \textit{effective} soldiers.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACCESS

access
}
\vspace*{\stretch{1}}
\begin{center}
ACCESS n. \textipa{[\textprimstress \ae kses]}
\end{center}
1. (to)接近（或进入）的机会，享用机会

All students have \textit{access} to the library.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LIABILITY

liability
}
\vspace*{\stretch{1}}
\begin{center}
LIABILITY n. \textipa{[\textsecstress lai\textschwa \textprimstress bil\textschwa iti]}
\end{center}
1. 不利条件，妨碍的人（或物）

Shyness is a \textit{liability} in politics.

2. [pl.]负债，债务

Heavy \textit{liabilities} forced the company into bankruptcy.

3. 责任

He accepted \textit{liability} for the damage done to the car.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
PRODUCTIVE

productive
}
\vspace*{\stretch{1}}
\begin{center}
PRODUCTIVE a. \textipa{[pr\textschwa \textprimstress d\textturnv ktiv]}
\end{center}
1. 多产的，富饶的

\textit{productive} fishing waters

2. 富有成效的

Your work in office has not been very \textit{productive}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STABILIZE/-ISE

stabilize/-ise
}
\vspace*{\stretch{1}}
\begin{center}
STABILIZE/-ISE v. \textipa{[\textprimstress steibilaiz]}
\end{center}
1. （使）稳定，（使）稳固

The price of coffee has been rising and falling sharply but has now been \textit{stabilized}.

\vspace*{\stretch{1}}
\end{flashcard}
