% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
INTELLIGENCE

intelligence
}
\vspace*{\stretch{1}}
\begin{center}
INTELLIGENCE n. \textipa{[in\textprimstress telid\textyogh \textschwa ns]}
\end{center}
1. 智力，智慧，理解力

He lacks \textit{intelligence}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
LIKELY

likely
}
\vspace*{\stretch{1}}
\begin{center}
LIKELY a. \textipa{[\textprimstress laikli]}
\end{center}
1. 可能的，有希望的

He is \textit{likely} to do something wrong.

2. 适合的

This is a \textit{likely} place to fish.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RELATIONSHIP

relationship
}
\vspace*{\stretch{1}}
\begin{center}
RELATIONSHIP n. \textipa{[ri\textprimstress lei\textesh \textschwa n\textesh ip]}
\end{center}
1. 关系，关联

What is the \textit{relationship} of crime to poverty?

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
OBSERVE

observe
}
\vspace*{\stretch{1}}
\begin{center}
OBSERVE vt. \textipa{[\textschwa b\textprimstress z\textschwa \textlengthmark v]}
\end{center}
1. 注意到，观察到

She pretended not to \textit{observe} it.

2. 说，评论

The speaker \textit{observed} that times had changed.

3. 遵守，奉行

All these rules must be strictly \textit{observed}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ASPECT

aspect
}
\vspace*{\stretch{1}}
\begin{center}
ASPECT n. \textipa{[\textprimstress \ae spekt]}
\end{center}
1. 方面

We must consider a problem in all its \textit{aspects}.

2. （建筑物的）朝向，方向

The house has a southern \textit{aspect}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COURT

court
}
\vspace*{\stretch{1}}
\begin{center}
COURT n. \textipa{[k\textopeno \textlengthmark t]}
\end{center}
1. 法庭，法院

The \textit{court} found him guilty.

2. 球场

They are practicing volleyball in the \textit{court}.

3. 宫廷，宫室

The \textit{court} has decided against the alliance.

4. 庭院，院子

The castle has a large \textit{court}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
FACTOR

factor
}
\vspace*{\stretch{1}}
\begin{center}
FACTOR n. \textipa{[\textprimstress f\ae kt\textschwa]}
\end{center}
1. 因素，要素

Health is a \textit{factor} of happiness.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
STYLE

style
}
\vspace*{\stretch{1}}
\begin{center}
STYLE n. \textipa{[stail]}
\end{center}
1. 风格，文体

His prose \textit{style} is perfect---so sincere and simple!

2. 式样，类型

They sell hats in all sizes and \textit{styles}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TRIVIAL

trivial
}
\vspace*{\stretch{1}}
\begin{center}
TRIVIAL a. \textipa{[\textprimstress trivi\textschwa l]}
\end{center}
1. 琐碎的，不重要的

He often speaks only of \textit{trivial} matters.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IMMUNE

immune
}
\vspace*{\stretch{1}}
\begin{center}
IMMUNE a. \textipa{[i\textprimstress mju\textlengthmark n]}
\end{center}
1. 免疫的，有免疫力的

We are \textit{immune} to smallpox.

2. 受影响的

We are not \textit{immune} to the influences around us.

3. 免除的，豁免的

Nobody is \textit{immune} from criticism.

\vspace*{\stretch{1}}
\end{flashcard}
