% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
DECLINE

decline
}
\vspace*{\stretch{1}}
\begin{center}
DECLINE vi. vt. n. \textipa{[di\textprimstress klain]}
\end{center}
vi. 1. 下降，减少，衰落

Domestic production of oil will continue to \textit{decline}.

vi. 2. 谢绝

We sent him an invitation but he \textit{declined}.

vt. 1. 婉辞，谢绝

We \textit{declined} his offer of a lift.

n. 1. 下降，减少，衰落

The country's No. 1 killer, heart disease, is on the \textit{decline}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AVAILABLE

available
}
\vspace*{\stretch{1}}
\begin{center}
AVAILABLE a. \textipa{[\textschwa \textprimstress veil\textschwa bl]}
\end{center}
1. 可利用的，可获得的

We took the first \textit{available} plane.

2. 可取得联系的

If I am not \textit{available} when you phone, ask for my secretary.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CAREER

career
}
\vspace*{\stretch{1}}
\begin{center}
CAREER n. \textipa{[k\textschwa \textprimstress ri\textschwa]}
\end{center}
1. 生涯，职业

Washington's \textit{career} as a soldier.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
UNIVERSE

universe
}
\vspace*{\stretch{1}}
\begin{center}
UNIVERSE n. \textipa{[\textprimstress ju\textlengthmark niv\textschwa \textlengthmark s]}
\end{center}
1. 宇宙，万物，世界

They thought the Earth was the centre of the \textit{universe}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RESIDENT

resident
}
\vspace*{\stretch{1}}
\begin{center}
RESIDENT n. a. \textipa{[\textprimstress rezid\textschwa nt]}
\end{center}
n. 1. 居民，定居者

Chinese \textit{residents} in America.

a. 1. 居住的，住校的，住院的

Since 1989 she has been \textit{resident} abroad.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
IDEAL

ideal
}
\vspace*{\stretch{1}}
\begin{center}
IDEAL a. n. \textipa{[ai\textprimstress di\textschwa l]}
\end{center}
a. 1. 理想的，完满的

an \textit{ideal} marriage

n. 1. 理想

He has a lofty \textit{ideal}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COLLIDE

collide
}
\vspace*{\stretch{1}}
\begin{center}
COLLIDE vi. \textipa{[k\textschwa \textprimstress laid]}
\end{center}
1. 碰撞，互撞

The car \textit{collided} with the truck./The car and the truck \textit{collided}.

2. 冲突，抵触

Their minds were constantly \textit{colliding} in endless arguments.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMPLY

comply
}
\vspace*{\stretch{1}}
\begin{center}
COMPLY vt. \textipa{[k\textschwa m\textprimstress plai]}
\end{center}
1. (with)遵从，依从，服从

We couldn't \textit{comply} with your request.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUBSCRIBE

subscribe
}
\vspace*{\stretch{1}}
\begin{center}
SUBSCRIBE vi. vt. \textipa{[s\textschwa b\textprimstress skraib]}
\end{center}
vi. 1. (to)同意，赞成

I unreservedly \textit{subscribe} to your proposal.

vi. 2. 订阅，订购（书籍等）

All the periodicals to which the library \textit{subscribes} are to be ordered for a further year.

vt. 1. 捐助，赞助

\textit{subscribe} 5,000 pounds a year to an institution

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
TUITION

tuition
}
\vspace*{\stretch{1}}
\begin{center}
TUITION n. \textipa{[tju\textlengthmark \textprimstress i\textesh \textschwa n]}
\end{center}
1. （某一学科的）教学，讲授，指导

He gives \textit{tuition} in mathematics.

2. 学费

\textit{Tuition} has risen sharply.

\vspace*{\stretch{1}}
\end{flashcard}
