% ========== 01
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ACUTE

acute
}
\vspace*{\stretch{1}}
\begin{center}
ACUTE a. \textipa{[\textschwa \textprimstress kju\textlengthmark t]}
\end{center}
1. 严重的，激烈的

The long drought caused an \textit{acute} shortage of water.

2. 敏锐的

Dogs hava an \textit{acute} sense of smell.

3. 高音的，尖声的

Some sounds are so \textit{acute} that we cannot hear them.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 02
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
CONTRAST

contrast
}
\vspace*{\stretch{1}}
\begin{center}
CONTRAST n. \textipa{[\textprimstress k\textopeno ntr\ae st]}
\end{center}
1. 对比，对照

The \textit{contrast} between light and shade is striking in this picture.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 03
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EVOKE

evoke
}
\vspace*{\stretch{1}}
\begin{center}
EVOKE vt. \textipa{[i\textprimstress v\textschwa uk]}
\end{center}
1. 唤起，引起，使人想起

His comment \textit{evoked} protest from the listeners.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 04
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
ORIGINATE

originate
}
\vspace*{\stretch{1}}
\begin{center}
ORIGINATE vi. vt. \textipa{[\textschwa \textprimstress rid\textyogh \textschwa neit]}
\end{center}
vi. 1. 起源于，来自，产生

Her book \textit{originated} from a short story.

vt. 1. 引起，创始，开创

He is credited with \textit{originating} a new printing process.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 05
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
RELIANCE

reliance
}
\vspace*{\stretch{1}}
\begin{center}
RELIANCE n. \textipa{[ri\textprimstress lai\textschwa ns]}
\end{center}
1. 依靠，依赖

He has \textit{reliance} on his parents.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 06
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
EFFECTIVE

effective
}
\vspace*{\stretch{1}}
\begin{center}
EFFECTIVE a. \textipa{[i\textprimstress fektiv]}
\end{center}
1. 有效的，生效的，起作用的

They delayed the \textit{effective} date from June 6 to July 27.

2. 效果不错的

He spoke \textit{effective} Chinese.

3. 有战斗力的

The fort was held by about 100 \textit{effective} soldiers.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 07
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
SUPERMARKET

supermarket
}
\vspace*{\stretch{1}}
\begin{center}
SUPERMARKET n. \textipa{[\textprimstress sju\textlengthmark p\textschwa \textsecstress m\textscripta \textlengthmark kit]}
\end{center}
1. 超级市场

We buy food at the \textit{supermarket}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 08
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
AUTHENTIC

authentic
}
\vspace*{\stretch{1}}
\begin{center}
AUTHENTIC a. \textipa{[\textopeno \textlengthmark \textprimstress \texttheta entik]}
\end{center}
1. 真的，真正的

The eyewitness gave an \textit{authentic} account of the accident.

2. 可靠的，可信的

This is an \textit{authentic} news report.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 09
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
MINIATURE

miniature
}
\vspace*{\stretch{1}}
\begin{center}
MINIATURE a. n. \textipa{[\textprimstress minj\textschwa t\textesh \textschwa]}
\end{center}
a. 1. 小型的，微小的

The child was playing on the floor with his collection of \textit{miniature} farm animals.

n. 1. 微小的模型，缩影

Paris is France in \textit{miniature}.

\vspace*{\stretch{1}}
\end{flashcard}
% ========== 10
\begin{flashcard}[NOTHING SEEK, NOTHING FIND]{
COMMODITY

commodity
}
\vspace*{\stretch{1}}
\begin{center}
COMMODITY n. \textipa{[k\textschwa \textprimstress m\textopeno d\textschwa ti]}
\end{center}
1. 商品，货物

The \textit{commodity} boom departed nearly as quickly as it arrived.

\vspace*{\stretch{1}}
\end{flashcard}
